### 2023-02-03 src/tex/ms.tex
small updates

% Define document class
\documentclass[preprint]{aastex631}
\usepackage{showyourwork}

% Begin!
\begin{document}

\newcommand{\ergsec}{erg s$^{-1}$ cm$^{-2}$ $\mu$m$^{-1}$}

% Title
\title{Keck Near-Infrared Observations of Mab}

% Author list
\author{@emolter}

\author{Imke}

\author{Chris}

% Abstract with filler text
\begin{abstract}
We report the first near-infrared detection of Uranus's smallest known moon Mab, the presumed source of the blue and diffuse $\mu$ ring, using the NIRC2 instrument at Keck Observatory.
something about shift-and-stack
If the moon has an effective radius of 12 km as previously proposed based on HST data, its geometric albedo would be xx at 1.6 $\mu$m and phase angle 0.02$^\circ$, while if it has a radius of 6 km, its geometric albedo would be xx. Taken along with the HST albedo measurements, this implies Mab is (much fainter than / much brighter than / about the same as) expected in the near-infrared. We propose that this is due to ... (remember to talk about low phase angle and opposition surge somewhere). We also report (the first?) infrared photometry of Ophelia, (Cordelia?), and Perdita.
\end{abstract}

% Main body with filler text
\section{Introduction}
\label{s:intro}

Look in JWST proposal!

\section{Observations and Data Processing}
\label{s:observations}

This paper makes use of H-band data taken on 28 October 2019 by the narrow camera of the NIRC2 instrument coupled to the Adaptive Optics (AO) system at Keck Observatory, using Uranus itself for wavefront sensing \citep{wizinowich00, vandam04}. The same data were analyzed by \citet{paradis23}, so we refer the reader to that paper for a detailed description of the observation and data reduction procedures. The standard star was FS2 from the UKIRT Faint Standard Star list\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc/UKIRTstds.html}}, and standard photometric calibration procedures resulted in calibration constants $C_H = 8.87\times10^{-17}$ and $C_K = 9.11\times10^{-17}$ to convert from 1 count per second to 1 \ergsec. The uncertainty in the photometric calibration was estimated from the spread in measured fluxes from the standard star between frames. The value we find is 20\% in both filters, which is typical for NIRC2 observations \citep{depater14, molter19}.

Our full dataset consisted of 23 exposures of 120 seconds in H-band (1.6 $\mu$m) and 24 exposures of 120 seconds each in K-band (2.2 $\mu$m); these were all the frames taken on 28 October 2019 when Mab's expected position was inside the field of view of the narrow camera; see the left panel of Figure \ref{fig:detection}.
The proper motion of Mab is roughly 30 mas (3 pixels) per minute, which means that each frame had to be shifted relative to the previous one in accordance with Mab's expected vector of motion to improve the signal-to-noise ratio (SNR). This so-called ``shift-and-stack" technique has been used by other authors to improve the SNR of moving point sources, including to measure photometry of other small moons of Uranus \citep[][]{paradis19, paradis23}. Our shift-and-stack procedure differs in several ways from the one implemented by those authors, and we describe it fully in Appendix \ref{s:shiftandstack}. The application of shift-and-stack resulted in a single summed image representing an effective integration time of 2760 seconds on the expected position of Mab.

\begin{figure}
\includegraphics[width=0.5\textwidth]{figures/motion_on_detector.png}
\includegraphics[width=0.5\textwidth]{figures/detection_image.png}
\caption{\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected position of Mab in each of our 23 H-band exposures. The bright and faint point sources visible in the image are Miranda and Puck, respectively. \textbf{Right:} Detection of Mab using the shift-and-stack technique. The red arrow indicates the average distance and direction of Mab's motion across the detector during a single 2-minute exposure.\label{fig:detection}}
\end{figure}

\section{Results}
\label{s:results}

\subsection{Photometry of Mab}

An image of our detection of Mab is shown in the right panel of Figure \ref{fig:detection}. The moon appears slightly vertically extended because its proper motion was roughly 6 pixels per frame, moving approximately toward sky North. The detection is in a low-SNR regime, but we are confident that it is real for three reasons. First, a tentative detection of Mab can be made separately from the first 11 frames and the last 11 frames, meaning that an artefact in a single frame is not producing a false positive. Second, the detection is located in the appropriate position on the sky relative to Miranda and Puck. Third, we performed an experiment to test the false positive rate of our shift-and-stack procedure under the same scattered light and noise conditions as the data. In short, we added random offsets to the expected position of Mab in each frame, then performed the shift-and-stack procedure in the same way as we did for the true expected position. We repeated this procedure with different random offsets 100 times, and found that no noise spikes as bright as our Mab detection appeared in any of these 100 different stacks; see Appendix \ref{s:falsepositives} for more details.

Because Mab was detected at low SNR and within a substantial scattered light background, the flux in the wings of the PSF could not be accurately measured. We therefore determined the flux of Mab using a flux bootstrapping procedure similar to that applied to Keck-observed point sources by many other authors \citep[e.g.,]{gibbard05, molter19, paradis23}, the specifics of which we summarize in Appendix \ref{s:photometry}. We find the total flux of Mab to be $(5.6 \pm 1.2)\times10^{-16}$ \ergsec, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the flux bootstrapping error (see Appendix \ref{s:photometry}) and the 20\% photometric calibration error. This flux level corresponds to an integrated I/F of XX km$^2$ at 1.6 $\mu$m, where the integrated I/F is defined as the sky-projected area the moon would have if it were a perfect Lambertian reflector \citep[i.e., a geometric albedo of unity][]{karkoschka01}. Note that the Sun-target-observer phase angle of these observations was only 0.02$^\circ$, so the opposition effect was likely substantial, as discussed more in Section \ref{s:discussion}.

We did not detect Mab in K-band. Nevertheless, we set an upper limit on Mab's K-band brightness of 
XX \ergsec. One must exercise caution when determining an upper limit for a point source that has moved by a substantial fraction of a resolution element during a single exposure because the target no longer appears to be a point source. HOW TO DO THIS PROPERLY?

\subsection{Photometry of Other Moons}

We report the detection of Ophelia in H- and K-band and Perdita in H-band [CHECK K-BAND AGAIN].
Something about Cordelia! do we actually see it?
tie in story about median subtraction of frames
Try Cupid again?

\section{Discussion}
\label{s:discussion}

The photometric model of \citet{karkoschka01} defines the I/F of a moon as the product of four normalized functions and a constant:
\begin{equation}
	\label{eq:if}
	I/F(l, \alpha, \lambda) = f_1(l) f_2(\alpha) f_3(\lambda) f_4(\lambda) (I/F)_0
\end{equation}
where $f_1(l)$ is the lightcurve as a function of orbital longitude $l$ with an orbital average of unity, $f_2(\alpha)$ is the phase function scaled to unity at phase angle $\alpha = 0$, $f_3(\lambda)$ is the solar spectrum at the observed wavelength $\lambda$ scaled to unity at 550 nm, $f_4(\lambda)$ is the band/continuum ratio, used to account for wavelength-dependent absorption features in the spectrum of the moon, and $(I/F)_0$ is the reflectivity at $\alpha = 0$ and $\lambda = 550$ nm, averaged over orbital longitude.

Use the above to contextualize Showalter observations, Sam's upper limit, and this detection in H-band but not K-band.

Sam's upper limit

What does it say about mu ring?

Something perhaps about orbital stability of Mab (if the offset from its expected position is real)

\acknowledgements

acknowledge Keck - look this up

\appendix

\section{Shift-and-Stack Procedure}
\label{s:shiftandstack}

To improve the SNR on Mab, individual 120-second frames were shifted according to the expected position of the moon relative to Uranus and then co-added; details of this procedure are presented here. First, we aligned the position of Uranus in all the frames using the \texttt{chi2\_shift} function of the \texttt{Astropy}-affiliated \texttt{image\_registration} Python package\footnote{\url{https://github.com/keflavich/image_registration}}, which implements the single-step discrete Fourier transform (DFT) algorithm for efficient sub-pixel image registration \citep{guizarsicairos08}. In K-band, cloud features and moons are brighter than the planet's disk, so we first applied the Canny edge-detection filter using the \texttt{skimage} Python package \citep{skimage14} to enhance the rings of Uranus, then ran \texttt{chi2\_shift} on those edges. This alignment method was found to produce very sharp stacked images of the rings, so we were confident that it was aligning the frames accurately. The implementation of this alignment step permitted us to co-add all three observing blocks shown in Figure \ref{fig:detection}, between which Uranus was repositioned on the detector by tens of pixels, and is the most important difference between our procedure and that of \citet{paradis19, paradis23}.  Second, we found the median of these planet-aligned frames and subtracted it from each frame; this removes the signal of non-moving sources (in this case, the planet and rings), decreasing the effects of scattered light. Third, the expected offset between Mab and Uranus at the time of each exposure (start time plus half the integration time) was taken from JPL Horizons\footnote{\url{https://ssd.jpl.nasa.gov/horizons/app.html\#/}}, accessed using the \texttt{Astroquery} Python package \citep{ginsburg19}. We converted the expected x,y offset from units of arcseconds to pixels assuming the pixel scale of the NIRC2 narrow camera to be 0.009971\arcsec \citep{service16} and taking the distance to Uranus from the Horizons ephemeris. Finally, we applied the shifts using a 2-D fast Fourier transform (FFT) sub-pixel image shift, again implemented with \texttt{image\_registration}, and summed all the frames.

\section{Flux Bootstrapping Technique}
\label{s:bootstrapping}

Using the \texttt{astropy}-affiliated \texttt{photutils} package \cite{}, we measured the total flux inside many circular apertures of different radii $r_i$ centered on Mab; let us call Mab's flux for the $i$th radius $F_{M i}$. We then measured the flux inside apertures of the same size but centered on the standard star; call these $F_{\star i}$. Comparing $F_{\star i}$ with the true flux of the standard star $F_\star$ (as measured in a very large aperture of radius $\gtrsim$100 pixels) yielded a correction for the wings of the PSF for a given value of $r_{i}$, given by simply $C_{psf} = F_{\star i}/F_\star$. The flux of the background must also be subtracted in order to accurately determine $F_{M i}$; we defined the background region using a circular annulus centered on Mab with inner radius $r_i + 5$ pixels and outer radius $r_o$. The background flux level $F_{B o}$ was taken to be the median of pixels within the background annulus multiplied by the area of the Mab aperture $\pi r_i^2$. We also varied $r_o$ over a range of values to test the sensitivity of our flux estimate to the choice of background region. The flux of Mab $F_{i,o}$ for a given $r_i, r_o$ pair is given by $F_M = (F_{M i} - F_{B o}) / C_{psf}$, and the value of $F_{i,o}$ is displayed as a function of $r_i$ and $r_o$ in Figure \ref{fig:wing}. The final flux estimate of Mab is given by the mean of $F_{i,o}$ over a reasonable range of $r_i$ and $r_o$ values, and the uncertainty is given by the standard deviation of $F_{i,o}$, which is $\approx$9\%. (This 9\% error is multiplied in quadrature with the typical 20\% flux calibration error from standard star observations with Keck). We chose smaller values of $r_i$ than \citet{paradis23} because the SNR of our Mab detection is much lower than the SNR of the moon detections shown in that paper.

\begin{figure}
\includegraphics[width=0.3\textwidth]{figures/example_aperture.png}
\includegraphics[width=0.7\textwidth]{figures/photometry_vs_region.png}
\caption{\textbf{Left:} Example aperture (solid blue line) and background annulus (dot-dashed red line) centered on Mab. The values of $r_i$ and $r_o$ in this example are 7 and 45 pixels, respectively. \textbf{Right:} Derived flux of Mab as a function of $r_i$ and $r_o$.\label{fig:wing}}
\end{figure}

\section{False Positive Rate Experiment}
\label{s:falsepositives}

Our detection of Mab has a low SNR, and the moon was located in the lower-left quadrant of the NIRC2 NARROW camera, which is known to have non-Gaussianity in its noise statistics [CITE]. It is therefore natural to wonder whether the shift-and-stack technique is somehow injecting false positives by stacking noise spikes atop one another. To test whether this is the case, we performed an experiment to test the false positive rate within the true detector noise and scattered light environment of the data, as follows. The expected position of Mab was shifted by a random x,y offset of mean amplitude 20 pixels in each frame, then the shift-and-stack algorithm was re-run assuming these new randomly-selected shifts and the output frame was saved. This experiment was repeated 100 times with different random offsets applied. We then searched for point sources in these 100 test frames by applying a center-surround filter with an FWHM of 2 pixels\footnote{this corresponds roughly to the diffraction-limited beam size of Keck in H-band}, then binned the filtered images by a factor of 2 in each direction. Finally, we computed the amplitude of the brightest pixel in each binned frame in units of the RMS noise of the input image. This yielded a rough estimate of the signal-to-noise ratio of that peak. Identical filtering, binning, and SNR calculations were run on the real data. The detection of Mab in the real data was found to have a higher SNR than any peak in any of the 100 test frames (see Figure \ref{fig:randomstack}). Based on this experiment, Mab was detected at the 7$\sigma$ level; however, it can be seen in panel (b) of Figure \ref{fig:randomstack}

\begin{figure}
\includegraphics[width=1.0\textwidth]{figures/random_stack_experiment.png}
\caption{Results of the false positives experiment. \textbf{(a)} Detection of Mab shown in Figure \ref{fig:detection}. \textbf{(b)} Panel (a) after filtering and binning were applied. \textbf{(c)} \label{fig:randomstack}}
\end{figure}

\bibliography{references}

\end{document}

### 2023-02-04 src/tex/ms.tex
finalized most of the figures

@@
 
-\newcommand{\ergsec}{erg s$^{-1}$ cm$^{-2}$ $\mu$m$^{-1}$}
+\newcommand{\ergsec}{erg s$^{-1}$ cm$^{-2}$ $\mu$m$^{-1}$\ }
 
@@
 
-% Abstract with filler text
 \begin{abstract}
@@
 
-Look in JWST proposal!
+something about the circumplanetary environment of Uranus
+
+% does the below text fit in anywhere?
+The small regular moons comprising the Portia group in the Uranian system represent the most densely-packed set of satellites known, with semimajor axis separations of 3\% on average \citep{showalter20}; as such, the system is predicted to be chaotic, with collisions occurring on 10$^5$-10$^7$-year timescales \citep{duncan97, french12}.
+Indeed, the faint dusty $\nu$ ring, situated between the orbits of Portia and Rosalind, has been proposed to be the remnant of such a collision.
+Due in part to this small orbital spacing, the Uranian satellites affect each other's geology via dust transport in the circumplanetary environment.
+For example, dust deposition from Uranus's outer irregular satellites has been invoked to explain spectral reddening of the leading hemispheres of Ariel, Umbriel, Titania, and Oberon \citep{cartwright18}.
+Material transport is important for understanding the surfaces of Miranda, Puck, and the smaller inner moons, too, but these processes are less well-studied.
+Puck's leading hemisphere has a significantly bluer spectral slope than its trailing hemisphere, meaning that it may be sweeping up material from the $\mu$ ring \citep{french17}, but this has not been confirmed.
+%this is a DPS abstract - is there a better reference?
+Unusually low depth/diameter ratios of craters on the potential ocean world Miranda suggest the deposition of a $\sim$1 km thick regolith \citep{cartwright21, beddingfield22}.
+Those authors propose three possible sources of the regolith material: deposition from the $\mu$ ring, plume deposits from a subsurface ocean, and/or giant impact ejecta.
+One sentence here linking these paragraphs
+
+Uranus's tiny moon Mab is embedded in the faint, diffuse $\mu$ ring, the only ring in the solar system with a blue spectrum other than Saturn's E ring, which is sourced from Enceladus's cryovolcanism \citep{depater06}.
+The E~ring is blue due to its abundance of tiny ($\lesssim$1 $\mu$m) particles and paucity of larger grains \citep{showalter91, depater04, hillier07}.
+While active cryovolcanism on such a small body as Mab seems highly unlikely, alternative theories for the formation and maintenance of the $\mu$ ring remain unconstrained by data.
+Mab has been proposed to be outbursting like the active Centaur Echeclus, with the blue color of the $\mu$ ring attributable not to small particle sizes but to a high abundance of carbon-rich organic matter \citep{seccull19}.
+Alternatively, interplanetary dust and/or charged plasma impacting Mab's surface may liberate enough particles to form the $\mu$ ring.
+To explain the blue color, the latter scenario relies on theoretical and numerical simulation expectations that $\sim$1 $\mu$m particles are more likely than larger particles to disperse into a ring (instead of re-accreting to the planet) under the combined influences of gravity, radiation pressure, and electromagnetic forces \citep{horanyi92, sfair09, sfair12}.
+In any case, the physical properties of this unusual moon are of interest for studies of interactions between airless surfaces and the interplanetary environment, the origin and dynamical evolution of circumplanetary dust, and the formation and evolution of small solar system bodies.
+
+The radius and albedo of Mab remain under debate.
+Based on HST observations, \citet{showalter06} proposed two end-member cases: Mab has a $\sim$6 km radius with a Miranda-like icy surface and an albedo of $\sim$0.46; or Mab has a $\sim$12 km radius and an albedo of $\sim$0.1, indicating the presence of dark organic compounds on its surface like its other nearest neighbor, Puck.
+However, a sensitive near-infrared search with Keck did not detect the moon, leading to the proposal that Mab's radius is $\lesssim$6 km and as dark at wavelengths from 1.6-2.4 $\mu$m as Uranus's inner main rings \citep[albedo $\sim$0.05;][]{paradis19, paradis23}.
+Strong near-IR absorption from water ice could partially account for this darkening; however, the decrease in brightness is not expected to exceed 50\% even for a very icy body \citep[c.f.
+Haumea, one of the purest amorphous ice surfaces in the solar system;][]{gourgeot16}.
+
+re-word the way Paradis is talked about above
+
+Here we present the first observations of Mab at near-infrared wavelengths.
+Our dataset and data proceessing steps are described in Section \ref{s:observations}.
+We present photometry of Mab, as well as Cordelia, Ophelia, and Perdita,
 
@@
 
-This paper makes use of H-band data taken on 28 October 2019 by the narrow camera of the NIRC2 instrument coupled to the Adaptive Optics (AO) system at Keck Observatory, using Uranus itself for wavefront sensing \citep{wizinowich00, vandam04}.
+This paper makes use of H- and K-band data taken on 28 October 2019 by the narrow camera of the NIRC2 instrument coupled to the Adaptive Optics (AO) system at Keck Observatory, using Uranus itself for wavefront sensing \citep{wizinowich00, vandam04}.
 The same data were analyzed by \citet{paradis23}, so we refer the reader to that paper for a detailed description of the observation and data reduction procedures.
-The standard star was FS2 from the UKIRT Faint Standard Star list\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc/UKIRTstds.html}}, and standard photometric calibration procedures resulted in calibration constants $C_H = 8.87\times10^{-17}$ and $C_K = 9.11\times10^{-17}$ to convert from 1 count per second to 1 \ergsec.
+The standard star was FS2 from the UKIRT Faint Standard Star list,\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc/UKIRTstds.html}} and standard photometric calibration procedures resulted in calibration constants $C_H = 8.87\times10^{-17}$ and $C_K = 9.11\times10^{-17}$ to convert from 1 count per second to 1 \ergsec.
 The uncertainty in the photometric calibration was estimated from the spread in measured fluxes from the standard star between frames.
-The value we find is 20\% in both filters, which is typical for NIRC2 observations \citep{depater14, molter19}.
+The value we found was 20\% in both filters, which is typical for NIRC2 observations \citep{depater14, molter19}.
 
-Our full dataset consisted of 23 exposures of 120 seconds in H-band (1.6 $\mu$m) and 24 exposures of 120 seconds each in K-band (2.2 $\mu$m); these were all the frames taken on 28 October 2019 when Mab's expected position was inside the field of view of the narrow camera; see the left panel of Figure \ref{fig:detection}.
+Our full dataset consisted of 23 exposures of 120 seconds each in H-band (1.6 $\mu$m) and 24 exposures of 120 seconds each in K-band (2.2 $\mu$m); these were all the frames taken on 28 October 2019 in which Mab's expected position was inside the field of view of the narrow camera; see the left panel of Figure \ref{fig:detection}.
 The proper motion of Mab is roughly 30 mas (3 pixels) per minute, which means that each frame had to be shifted relative to the previous one in accordance with Mab's expected vector of motion to improve the signal-to-noise ratio (SNR).
-This so-called ``shift-and-stack" technique has been used by other authors to improve the SNR of moving point sources, including to measure photometry of other small moons of Uranus \citep[][]{paradis19, paradis23}.
-Our shift-and-stack procedure differs in several ways from the one implemented by those authors, and we describe it fully in Appendix \ref{s:shiftandstack}.
-The application of shift-and-stack resulted in a single summed image representing an effective integration time of 2760 seconds on the expected position of Mab.
+This so-called ``shift-and-stack" technique has been used by other authors to improve the SNR of moving point sources, including to measure photometry of other small moons of Uranus with NIRC2 \citep[][]{paradis19, paradis23}.
+Our shift-and-stack procedure differs in several ways from the one implemented by those authors, though, and we describe it fully in Appendix \ref{s:shiftandstack}.
+The application of shift-and-stack resulted in one stacked image per filter at the expected position of Mab, representing effective integration times of 2760 seconds in H-band and 2880 seconds in K-band.
 
@@
 \includegraphics[width=0.5\textwidth]{figures/motion_on_detector.png}
-\includegraphics[width=0.5\textwidth]{figures/detection_image.png}
+\includegraphics[width=0.5\textwidth]{figures/detection_images_Mab.png}
 \caption{\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected position of Mab in each of our 23 H-band exposures.
 The bright and faint point sources visible in the image are Miranda and Puck, respectively.
-\textbf{Right:} Detection of Mab using the shift-and-stack technique.
-The red arrow indicates the average distance and direction of Mab's motion across the detector during a single 2-minute exposure.\label{fig:detection}}
+\textbf{Right:} Detection of Mab in H-band (top panel) and tentative detection in K-band (bottom panel) using the shift-and-stack technique.\label{fig:detection}}
 \end{figure}
@@
 
-An image of our detection of Mab is shown in the right panel of Figure \ref{fig:detection}.
-The moon appears slightly vertically extended because its proper motion was roughly 6 pixels per frame, moving approximately toward sky North.
+An image of our H-band detection of Mab is shown in the upper right panel of Figure \ref{fig:detection}.
+The moon appears slightly vertically extended because its proper motion was roughly 6 pixels per 120-second frame, moving approximately toward sky North.
 The detection is in a low-SNR regime, but we are confident that it is real for three reasons.
-First, a tentative detection of Mab can be made separately from the first 11 frames and the last 11 frames, meaning that an artefact in a single frame is not producing a false positive.
-Second, the detection is located in the appropriate position on the sky relative to Miranda and Puck.
+First, a tentative detection of Mab can be made separately from the first 11 frames and the last 11 frames, meaning that an artefact in a single frame or 8-frame group is not producing a false positive.
+Second, the detection is located in the appropriate position on the sky relative to Miranda and Puck, as discussed below.
 Third, we performed an experiment to test the false positive rate of our shift-and-stack procedure under the same scattered light and noise conditions as the data.
-In short, we added random offsets to the expected position of Mab in each frame, then performed the shift-and-stack procedure in the same way as we did for the true expected position.
-We repeated this procedure with different random offsets 100 times, and found that no noise spikes as bright as our Mab detection appeared in any of these 100 different stacks; see Appendix \ref{s:falsepositives} for more details.
+In short, we added random offsets to the expected position of Mab in each frame, then carried out shift-and-stack in the same way as we did for the true expected position.
+We repeated this procedure with different random offsets 100 times, and found that no noise spikes as bright as our Mab detection appeared anywhere in any of these 100 different stacks; see Appendix \ref{s:falsepositives} for more details.
 
 Because Mab was detected at low SNR and within a substantial scattered light background, the flux in the wings of the PSF could not be accurately measured.
-We therefore determined the flux of Mab using a flux bootstrapping procedure similar to that applied to Keck-observed point sources by many other authors \citep[e.g.,]{gibbard05, molter19, paradis23}, the specifics of which we summarize in Appendix \ref{s:photometry}.
-We find the total flux of Mab to be $(5.6 \pm 1.2)\times10^{-16}$ \ergsec, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the flux bootstrapping error (see Appendix \ref{s:photometry}) and the 20\% photometric calibration error.
+We therefore determined the flux of Mab using a flux bootstrapping procedure similar to that applied to Keck-observed point sources by many other authors \citep[e.g.,][]{gibbard05, molter19, paradis23}, the specifics of which we summarize in Appendix \ref{s:bootstrapping}.
+We find the total flux of Mab to be $(5.2 \pm 1.7)\times10^{-16}$ \ergsec in H-band, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the flux bootstrapping error (see Appendix \ref{s:bootstrapping}) and the 20\% photometric calibration error.
 This flux level corresponds to an integrated I/F of XX km$^2$ at 1.6 $\mu$m, where the integrated I/F is defined as the sky-projected area the moon would have if it were a perfect Lambertian reflector \citep[i.e., a geometric albedo of unity][]{karkoschka01}.
@@
 
-We did not detect Mab in K-band. Nevertheless, we set an upper limit on Mab's K-band brightness of 
-XX \ergsec.
-One must exercise caution when determining an upper limit for a point source that has moved by a substantial fraction of a resolution element during a single exposure because the target no longer appears to be a point source.
-HOW TO DO THIS PROPERLY?
+The observed position of Mab is the same as expected based on the orbital parameters in the JPL Horizons system\footnote{\url{https://ssd.jpl.nasa.gov/horizons/app.html\#/}} to within one Keck resolution element; see Figure \ref{fig:astrometry}.
+We determined this based on the relative positions of Mab, Miranda, and Puck, the latter two of which can be seen easily in a single 120-second frame.
+The advantage of using the positions of other moons as a reference for astrometry is that it does not depend on a navigation solution for the planet's disk.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figures/expected_position_urh_Mab_oneframe.png}
+\includegraphics[width=0.5\textwidth]{figures/expected_position_urh_Mab.png}
+\caption{Two visualizations of Mab's expected position.
+\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected relative positions of Mab, Miranda, and Puck (red arrows) as well as the detected position of Mab (blue dot).
+The expected vector of motion of Mab is also overlain (blue arrow).
+\textbf{Right:} The same shifted-and-stacked detection image of Mab shown in the right panel of Figure \ref{fig:detection}, but zoomed out and stretched to show the apparent trajectories of Puck and Miranda.
+Mab's position is marked with a purple circle.
+The expected motion of Puck and Miranda relative to Mab are plotted as red and orange lines, respectively.
+Miranda is still overexposed in this image stretch, so the brightest pixels in Miranda's track are highlighted in cyan.\label{fig:astrometry}}
+\end{figure}
+
+A very faint region of positive flux was observed at the expected position of Mab after stacking the K-band data (see Figure \ref{fig:detection}).
+This feature is not clearly distinguishable by eye from positive noise spikes elsewhere in the frame.
+The false positive rate experiment discussed in Appendix \ref{s:falsepositives} shows that a noise spike of similar brightness would appear within $\sim$50 pixels of the expected position $\sim$8\% of the time.
+However, our uncertainty in Mab's position is roughly one H-band PSF FWHM, or $\sim$4 pixels, because we detected Mab at the expected position in H-band.
+We therefore label this a tentative detection.
+Photometry was performed in an identical way as for the H-band data, and we found a flux of $(3.6 \pm 0.9)\times10^{-16}$ \ergsec.
 
@@
 Something about Cordelia! do we actually see it?
-tie in story about median subtraction of frames
-Try Cupid again?
+tie in story about median subtraction of frames.
+Try Cupid again.
 
@@
 \end{equation}
-where $f_1(l)$ is the lightcurve as a function of orbital longitude $l$ with an orbital average of unity, $f_2(\alpha)$ is the phase function scaled to unity at phase angle $\alpha = 0$, $f_3(\lambda)$ is the solar spectrum at the observed wavelength $\lambda$ scaled to unity at 550 nm, $f_4(\lambda)$ is the band/continuum ratio, used to account for wavelength-dependent absorption features in the spectrum of the moon, and $(I/F)_0$ is the reflectivity at $\alpha = 0$ and $\lambda = 550$ nm, averaged over orbital longitude.
+where $f_1(l)$ is the lightcurve as a function of orbital longitude $l$ with an orbital average of unity, $f_2(\alpha)$ is the phase function scaled to unity at phase angle $\alpha = 0$, $f_3(\lambda)$ is the solar spectrum (the ``continuum'') at the observed wavelength $\lambda$ scaled to unity at 550 nm, $f_4(\lambda)$ is the band/continuum ratio, used to account for wavelength-dependent absorption features in the spectrum of the moon, and $(I/F)_0$ is the reflectivity at $\alpha = 0$ and $\lambda = 550$ nm, averaged over orbital longitude.
 
-Use the above to contextualize Showalter observations, Sam's upper limit, and this detection in H-band but not K-band.
+Use the above to contextualize Showalter observations, Sam's upper limit, and the observed brightness in H-band vs K-band.
 
@@
 
-Something perhaps about orbital stability of Mab (if the offset from its expected position is real)
+Something perhaps about orbital stability of Mab
 
-\acknowledgements
+\begin{acknowledgements}
 
-acknowledge Keck - look this up
+The data presented herein were obtained at the W.
+M.
+Keck Observatory, which is operated as a scientific partnership among the California Institute of Technology, the University of California and the National Aeronautics and Space Administration.
+The Observatory was made possible by the generous financial support of the W.
+M.
+Keck Foundation.
+
+The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Maunakea has always had within the indigenous Hawaiian community.
+We are most fortunate to have the opportunity to conduct observations from this mountain.
+
+\end{acknowledgements}
 
@@
 To improve the SNR on Mab, individual 120-second frames were shifted according to the expected position of the moon relative to Uranus and then co-added; details of this procedure are presented here.
+The accuracy of the shift-and-stack procedure depends sensitively on the rotation angle of the detector, so we corrected for the 0.26$^\circ$ angular offset between NIRC2's sky North position and true sky North before starting \citep{service16}.
 First, we aligned the position of Uranus in all the frames using the \texttt{chi2\_shift} function of the \texttt{Astropy}-affiliated \texttt{image\_registration} Python package\footnote{\url{https://github.com/keflavich/image_registration}}, which implements the single-step discrete Fourier transform (DFT) algorithm for efficient sub-pixel image registration \citep{guizarsicairos08}.
-In K-band, cloud features and moons are brighter than the planet's disk, so we first applied the Canny edge-detection filter using the \texttt{skimage} Python package \citep{skimage14} to enhance the rings of Uranus, then ran \texttt{chi2\_shift} on those edges.
+In K-band, cloud features and moons are brighter than the planet's disk, so we first applied a Canny edge-detection filter using the \texttt{skimage} Python package \citep{skimage14} to enhance the rings of Uranus, then ran \texttt{chi2\_shift} on those edges.
 This alignment method was found to produce very sharp stacked images of the rings, so we were confident that it was aligning the frames accurately.
-The implementation of this alignment step permitted us to co-add all three observing blocks shown in Figure \ref{fig:detection}, between which Uranus was repositioned on the detector by tens of pixels, and is the most important difference between our procedure and that of \citet{paradis19, paradis23}.
-Second, we found the median of these planet-aligned frames and subtracted it from each frame; this removes the signal of non-moving sources (in this case, the planet and rings), decreasing the effects of scattered light.
-Third, the expected offset between Mab and Uranus at the time of each exposure (start time plus half the integration time) was taken from JPL Horizons\footnote{\url{https://ssd.jpl.nasa.gov/horizons/app.html\#/}}, accessed using the \texttt{Astroquery} Python package \citep{ginsburg19}.
+The implementation of this alignment step permitted us to co-add all three H-band observing blocks (and two K-band observing blocks) shown in Figure \ref{fig:detection}, between which Uranus was repositioned on the detector by tens of pixels, and is the most important difference between our procedure and that of \citet{paradis19, paradis23}.
+Second, we found the median of these planet-aligned frames and subtracted it from each frame; this step suppresses the signal of non-moving sources (in this case, the planet and rings), decreasing the effects of scattered light.
+Third, the expected offset between Mab and Uranus at the time of each exposure (we define this as the start time plus half the exposure time) was taken from JPL Horizons, accessed using the \texttt{Astroquery} Python package \citep{ginsburg19}.
 We converted the expected x,y offset from units of arcseconds to pixels assuming the pixel scale of the NIRC2 narrow camera to be 0.009971\arcsec \citep{service16} and taking the distance to Uranus from the Horizons ephemeris.
@@
 
-Using the \texttt{astropy}-affiliated \texttt{photutils} package \cite{}, we measured the total flux inside many circular apertures of different radii $r_i$ centered on Mab; let us call Mab's flux for the $i$th radius $F_{M i}$.
+Using the \texttt{astropy}-affiliated \texttt{photutils} package \citep{photutils140}, we measured the total flux inside many circular apertures of different radii $r_i$ centered on Mab; let us call Mab's flux for the $i$th radius $F_{M i}$.
 We then measured the flux inside apertures of the same size but centered on the standard star; call these $F_{\star i}$.
@@
 
-Our detection of Mab has a low SNR, and the moon was located in the lower-left quadrant of the NIRC2 NARROW camera, which is known to have non-Gaussianity in its noise statistics [CITE].
+Our detection of Mab has a low SNR, and the moon was located in the lower-left quadrant of the NIRC2 NARROW camera, which is known to have non-Gaussianity in its noise statistics,\footnote{https://www2.keck.hawaii.edu/inst/nirc2/ObserversManual.html} including vertical stripes of correlated noise.
 It is therefore natural to wonder whether the shift-and-stack technique is somehow injecting false positives by stacking noise spikes atop one another.
@@
 This experiment was repeated 100 times with different random offsets applied.
-We then searched for point sources in these 100 test frames by applying a center-surround filter with an FWHM of 2 pixels\footnote{this corresponds roughly to the diffraction-limited beam size of Keck in H-band}, then binned the filtered images by a factor of 2 in each direction.
+We then searched for point sources in these 100 test stacks by applying a center-surround (difference-of-Gaussains) filter with an FWHM of 4 pixels for the inner Gaussian\footnote{this corresponds roughly to the diffraction-limited beam size of Keck in H-band} and an FWHM of 12 pixels for the outer Gaussian.
+The center-surround filter is the appropriate choice because it accentuates features at the desired spatial frequency and downweights low spatial frequency features.
+The visual systems of humans and other animals employ center-surround antagonism \citep{graham06}, so this technique is a reasonable proxy for ``by-eye'' detection.
+We then binned the filtered images by a factor of 2 in each direction.
 Finally, we computed the amplitude of the brightest pixel in each binned frame in units of the RMS noise of the input image.
@@
 Identical filtering, binning, and SNR calculations were run on the real data.
-The detection of Mab in the real data was found to have a higher SNR than any peak in any of the 100 test frames (see Figure \ref{fig:randomstack}).
-Based on this experiment, Mab was detected at the 7$\sigma$ level; however, it can be seen in panel (b) of Figure \ref{fig:randomstack}
+The detection of Mab in the real data was found to have a higher SNR than any peak in any of the 100 test frames in H-band (see Figure \ref{fig:randomstack}).
+In K-band, we find that a noise spike with an amplitude higher than our tentative detection is present in 8 out of 100 frames (Figure \ref{fig:randomstack_K}).
+However, because our tentative detection is in the correct position on the detector relative to Miranda and Puck, we feel justified in labeling it a tentative detection rather than a non-detection and extracting photometry.
+We tested other choices of inner and outer FWHM for the center-surround filter and different amounts of binning, and found that the results remained similar within reasonable ranges of these parameters.
+The SNR values reported in Figures \ref{fig:randomstack} and \ref{fig:randomstack_K} may look surprisingly high; note that they represent the detection level above the per-pixel RMS noise in the image, but these values do not correlate well with the true confidence level of a detection due to the substantial spatial correlation of the noise.
 
 \begin{figure}
-\includegraphics[width=1.0\textwidth]{figures/random_stack_experiment.png}
-\caption{Results of the false positives experiment.
+\includegraphics[width=1.0\textwidth]{figures/random_stack_experiment_Mab_H.png}
+\caption{Results of the false positive rate experiment for H band.
 \textbf{(a)} Detection of Mab shown in Figure \ref{fig:detection}.
 \textbf{(b)} Panel (a) after filtering and binning were applied.
-\textbf{(c)} \label{fig:randomstack}}
+\textbf{(c)} Example filtered and binned randomized stack.
+\textbf{(d)} Histogram of the SNR of the brightest pixel in the filtered and binned test frames; the real data are demarcated with a black dashed line.\label{fig:randomstack}}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1.0\textwidth]{figures/random_stack_experiment_Mab_K.png}
+\caption{Results of the false positive rate experiment for K band. See caption of Figure \ref{fig:randomstack} for a description. \label{fig:randomstack_K}}
 \end{figure}

### 2023-02-04 src/scripts/compute_if.py

@@ -7,5 +7,25 @@ import matplotlib.pyplot as plt
 Start with the best photometry of a moon in erg s-1 cm-1 um-1 units,
 determine the integrated I/F,
 determine the I/F for some assumed radii, like 6 km and 12 km
+
+use the Jupyter notebooks from the JWST proposal for help
 '''
 
+constants_dict = {
+    'Mab':{
+        'H':{'flux':5.2e-16, 'err':1.7e-16, }, 
+        'K':{'flux':3.6e-16, 'err':0.9e-16, }, 
+        },
+    'Ophelia':{
+        'H':{},
+        'K':{},
+        },
+    'Cordelia':{
+        'H':{},
+        'K':{},
+        },
+    'Perdita':{
+        'H':{},
+        'K':{},
+        },
+}

### 2023-02-04 src/scripts/detection_pretty_picture.py

@@ -23,50 +23,97 @@ is $\approx$6.2 pixels in the sky-North-Northeast direction.
 This is larger than Keck's diffraction-limited resolution of 40 mas (4 pixels) at 1.6 $\mu$m,
 so smearing is substantial in the N-S direction, as seen in Figure \ref{fig:detection}.
 "
+
+ready to ship!
 '''
 
-mab_loc = (683, 503)
-mab_loc_firsthalf = mab_loc
-#mab_loc_secondhalf = (767, 656) #these are not the correct numbers
+code = 'Mab'
+
+constants_dict = {
+    'Mab':{
+        'H':{'stem':'urh', 'coadds':6, 'xpos':187, 'ypos':395}, #urh156
+        'K':{'stem':'urk', 'coadds':4, 'xpos':188, 'ypos':307}, #urk146
+        },
+    'Ophelia':{
+        'H':{},
+        'K':{},
+        },
+    'Cordelia':{
+        'H':{},
+        'K':{},
+        },
+    'Perdita':{
+        'H':{},
+        'K':{},
+        },
+}
+
 pad_x = 50
 pad_y = pad_x
-average_motion = (-1.5348859518691143, 6.0000087209428985) #per exposure, from mab_path_on_detector.py
-
-hdul_full = fits.open(paths.data / 'results/urh_Mab_2019-10-28.fits')
-mab_loc_firsthalf = mab_loc
-hdul_firsthalf = fits.open(paths.data / 'results/urh_Mab_2019-10-28_firsthalf.fits')
-hdul_secondhalf = fits.open(paths.data / 'results/urh_Mab_2019-10-28_secondhalf.fits')
-#print(hdul_secondhalf[0].header['EXPSTART'])
-
-itime = hdul_full[0].header['ITIME'] / 6 # the 6 coadds per frame have already been accounted for, according to Imke
-data_full = hdul_full[0].data / itime 
-data_firsthalf = hdul_firsthalf[0].data
-data_secondhalf = hdul_secondhalf[0].data
 
 
-fig, ax0 = plt.subplots(1,1, figsize = (8, 8))
+fs = 14
+fig, axes = plt.subplots(2,1, figsize = (5.5, 8))
 
-cim0 = ax0.imshow(data_full, vmin = -5e-2, vmax = 10e-2, cmap='Greys_r')
-#ax1.imshow(data_firsthalf, vmin = -30, vmax = 50, cmap='Greys_r')
[…]

### 2023-02-04 src/scripts/mab_path_on_detector.py

@@ -17,13 +17,13 @@ imshow a single detector frame, then overplot the path Mab took
     one point per actual exposure
 determine the average Mab vector over a single exposure using data from Horizons
 compare that with the elongation of Mab
+
+ready to ship!
 '''
 
 # find filenames
 data_dir = paths.data / 'reduced/2019oct28'
 data_files = os.listdir(data_dir)
-filt = 'h'
-stem = f'ur{filt}'
 obscode = '568'
 code = 'Mab'
 date = '2019-10-28'
@@ -33,20 +33,10 @@ pixscale_arcsec = 0.009971 #arcsec
 req = 25559 #km
 rpol = 24973 #km
 
-fnames = [data_dir / s for s in data_files if s.startswith(stem)]
-
-# split into different observing blocks
-data_indices = np.array([int(s.split('.')[0][3:]) for s in data_files if s.startswith(stem)])
-sorti = np.argsort(data_indices)
-indices_sorted = np.sort(data_indices)
-diff = indices_sorted[1:] - indices_sorted[:-1]
-block_ends = np.argwhere(diff > 1).T[0]+1
-block_starts = np.concatenate([np.array([0]), block_ends])
-block_ends = np.concatenate([block_ends, np.array([len(fnames)])])
-fnames_sorted = np.array(fnames)[sorti]
-#select which observing blocks you want
-fnames = fnames_sorted[block_starts[5]+1:block_ends[7]] #Mab is found in block 5-7 for H-band
-#fnames = fnames_sorted[1:]
+constants_dict = {
+    'H':{'stem':'urh', 'reverse':True, 'canny':False, 'start_idx':41, 'end_idx':64}, #urh156
+        'K':{'stem':'urk', 'reverse':True, 'canny':True, 'start_idx':0, 'end_idx':24}, #urk146
+        }
 
 ## get ephemeris from Horizons. quantity 6 is the satellite relative position to parent in arcsec
 horizons_obj = Horizons(
@@ -57,44 +47,73 @@ horizons_obj = Horizons(
 ephem = horizons_obj.ephemerides(quantities=6).to_pandas()
 ephem = ephem.set_index(pd.DatetimeIndex(ephem["datetime_str"]))
 
-# find the x,y position and velocity at each time step
-pos_x, pos_y = [], []
-vec_x, vec_y = [], []
 exposure_starts = []
-for fname in fnames:
[…]

### 2023-02-04 src/scripts/perturbation_experiment.py

@@ -24,11 +24,9 @@ Making the frames was done at the bottom of shift_stack_uranus.py
     The detection of Mab in the real data was found to have a higher SNR than any peak 
     in any of the 100 test frames; see Figure \ref{fig:randomstack}."
 
-TO DO:
-- final decision about units and scaling of the filtered images
-    - is it a good idea to try to conserve flux?
-- put all the frames of the image on the same color scale, add a colorbar
-- add panel labels, (a) to (d)
+To do:
+make it do both filters in a loop in order to make both figs that go in the paper
+but otherwise it's ready to ship
 '''
 
 import numpy as np
@@ -40,17 +38,40 @@ from scipy.signal import medfilt2d, convolve2d
 import paths
 from skimage.filters import difference_of_gaussians
 
-fname_real = paths.data / 'results/urh_Mab_2019-10-28.fits'
+code = 'Mab'
+band = 'H'
+
+constants_dict = {
+    'Mab':{
+        'H':{'stem':'urh', 'xpos':187, 'ypos':395}, #urh156
+        'K':{'stem':'urk', 'xpos':188, 'ypos':307}, #urk146
+        },
+    'Ophelia':{
+        'H':{},
+        'K':{},
+        },
+    'Cordelia':{
+        'H':{},
+        'K':{},
+        },
+    'Perdita':{
+        'H':{},
+        'K':{},
+        },
+}
+
+stem = constants_dict[code][band]['stem']
+fname_real = paths.data / f'results/{stem}_{code}_2019-10-28.fits'
 fstem_experiment = paths.data / 'perturbation_experiment'
 hdul_real = fits.open(fname_real)
 data_real = hdul_real[0].data
-ypos = 507 
-xpos = 683
+ypos = constants_dict[code][band]['ypos']
+xpos = constants_dict[code][band]['xpos']
 box_x = 60
 box_y = 30
 
 # parameters of the center-surround
-fwhm_px = 5.0 #approx number of pixels of Keck diffraction limit
+fwhm_px = 4.0 #approx number of pixels of Keck diffraction limit
 sigma_inner = fwhm_px/2.35482004503
 sigma_outer = 3*sigma_inner
 
@@ -67,39 +88,27 @@ data_real = data_real[ypos-box_y:ypos+box_y, xpos-box_x:xpos+box_x]
[…]

### 2023-02-04 src/scripts/photometry.py

@@ -8,7 +8,7 @@ we compute the error on the photometry by using many inner and outer radii
 
 
 TO DO:
-- rewrite this to operate on all the moons we want to include
+- add data for all the moons we want to include
 - make this give ``final answers" and compile them into tables
 '''
 
@@ -20,18 +20,44 @@ from astropy import table
 import paths
 from scipy.interpolate import interp1d
 
-fname = paths.data / 'results/urh_Mab_2019-10-28.fits'
-ypos = 505   #503
-xpos = 683 #699
+code = 'Mab'
+band = 'H'
+
+photometry_constants_dict = {
+    'Mab':{
+        'H':{'stem':'urh', 'coadds':6, 'C1':8.87e-17, 'xpos':187, 'ypos':395}, #urh156
+        'K':{'stem':'urk', 'coadds':4, 'C1':6.46e-17, 'xpos':188, 'ypos':307}, #urk146
+        },
+    'Ophelia':{
+        'H':{},
+        'K':{},
+        },
+    'Cordelia':{
+        'H':{},
+        'K':{},
+        },
+    'Perdita':{
+        'H':{},
+        'K':{},
+        },
+}
+
+
+stem = photometry_constants_dict[code][band]['stem']
+n_coadds_raw = photometry_constants_dict[code][band]['coadds'] #apparently the "raw" images were already divided by the number of coadds so this is needed
+xpos = photometry_constants_dict[code][band]['xpos'] 
+ypos = photometry_constants_dict[code][band]['ypos'] 
+# Paradis et al conversion factors for 2019-10-28
+C1 = photometry_constants_dict[code][band]['C1']  # from cts s-1 to erg s-1 cm-2 um-1; see Paradis+23 Section 2.5.1
+
+fname = paths.data / f'results/{stem}_{code}_2019-10-28.fits'
 boxr = 50
 rinner = 7
 rmid = 12
 router = 45
-
-# Paradis et al conversion factors for 2019-10-28
-C1 = 8.87e-17 # from cts s-1 to erg s-1 cm-2 um-1; see Paradis+23 Section 2.5.1
 CU, CR = 1,1 # see Paradis+23 Section 2.5. this could be looked at later but for now it's ok
-n_coadds_raw = 6 #apparently the "raw" images were already divided by the number of coadds so this is needed
+
+
 
[…]

### 2023-02-04 src/scripts/psf_wing_correction.py

@@ -11,86 +11,92 @@ import paths
 '''
 Use standard star observations to compute the flux correction
     due to the fact that we miss the wings of the PSF when we determine the moon flux
+
+ready to ship!
 '''
 
-filt = "H"
-nsamples = 50
-ri0 = 3 #smallest moon aperture radius
-ri1 = 20 #largest moon aperture radius
-ro0 = 100 #star aperture radius to capture all star flux; also sets inner radius of noise annulus
-ro1 = 300
-noise_ann_width = 100 #width of noise annulus starting at ro
+show_figures = False
+for filt in ['H', 'K']:
 
-star_files = [paths.data / f"reduced/2019oct28" / s for s in os.listdir(paths.data / f"reduced/2019oct28/") if s.startswith(f'hd{filt}')]
-ris = np.linspace(ri0, ri1, nsamples)
-ros = np.linspace(ro0, ro1, nsamples)
-
-
-
-
-
-for k, fname in enumerate(star_files):
+    nsamples = 50
+    ri0 = 3 #smallest moon aperture radius
+    ri1 = 20 #largest moon aperture radius
+    ro0 = 100 #star aperture radius to capture all star flux; also sets inner radius of noise annulus
+    ro1 = 300
+    noise_ann_width = 100 #width of noise annulus starting at ro
     
-    hdul = fits.open(fname)
-    print(fname)
-    data = hdul[0].data
-    data[data>5800] = 0 #this removes bad pixels
-    star_pos = np.unravel_index(np.argmax(data), data.shape)[::-1]
-    print(star_pos, np.max(data))
+    star_files = [paths.data / f"reduced/2019oct28" / s for s in os.listdir(paths.data / f"reduced/2019oct28/") if s.startswith(f'hd{filt}')]
+    ris = np.linspace(ri0, ri1, nsamples)
+    ros = np.linspace(ro0, ro1, nsamples)
     
-    # flux from moon inner radius
-    moon_aps = np.array([aperture.CircularAperture(star_pos, r=ri) for ri in ris])
-    moon_areas = np.array([ap.area for ap in moon_aps])
-    moon_apsums = np.array([aperture.ApertureStats(data, ap).sum for ap in moon_aps])
     
-    # flux from star inner radius
-    star_aps = [aperture.CircularAperture(star_pos, r=ro) for ro in ros]
-    star_areas = [star_ap.area for star_ap in star_aps]
[…]

### 2023-02-04 src/scripts/relative_position_miranda_puck.py

@@ -2,6 +2,9 @@
 
 import numpy as np
 import matplotlib.pyplot as plt
+from matplotlib.colors import LogNorm
+from mpl_toolkits.axes_grid1.axes_divider import make_axes_locatable
+from matplotlib import cm
 from astropy.io import fits
 import paths
 import pandas as pd
@@ -18,28 +21,57 @@ See if that triangle matches the true position of Mab
 
 Second test: flip the problem by overlaying the expected path of Miranda and Puck relative to 
     Mab on top of the detection image
+
+To do: make this generically accept any small moon or band
 '''
 
-hdul = fits.open(paths.data / 'results/urh_Mab_2019-10-28_test3.fits')
-single_frame_hdul = fits.open(paths.data / 'reduced/2019oct28/urh156.fits')
-hdr = hdul[0].header
-stack_data = hdul[0].data
-frame_data = single_frame_hdul[0].data
+code = 'Mab'
+band = 'H'
 
-obsdate = hdr["DATE-OBS"].strip(", \n")
-obsdate = datetime.strftime(datetime.strptime(obsdate, "%Y-%m-%d"), "%Y-%b-%d")
-start_time = obsdate + " " + hdr["EXPSTART"][:5]
+constants_dict = {
+    'Mab':{
+        'H':{'stem':'urh', 'frameid':156, 'xpos':187, 'ypos':395, 'Miranda_pos':np.array([62, 481]), 'Puck_pos':np.array([301, 738]), 'Mab_motion':np.array([-0.200581686891951, 6.719486510881566])}, #urh156
+        'K':{'stem':'urk', 'frameid':146, 'xpos':188, 'ypos':307, 'Miranda_pos':np.array([54,403]), 'Puck_pos':np.array([267, 650]), 'Mab_motion':np.array([-0.9026175910138363, 6.518904823989544])}, #urk146
+        },
+    'Ophelia':{
+        'H':{},
+        'K':{},
+        },
+    'Cordelia':{
+        'H':{},
+        'K':{},
+        },
+    'Perdita':{
+        'H':{},
+        'K':{},
+        },
+}
+
 obscode = '568'
 date = '2019-10-28'
 tstart = date+' 00:00'
 tend = date+' 23:59'
 pixscale_arcsec = 0.009971 #arcsec
+stem = constants_dict[code][band]['stem']
+frameid = constants_dict[code][band]['frameid']
+
[…]

### 2023-02-04 src/scripts/shift_stack_uranus.py

@@ -2,9 +2,8 @@
 
 '''
 TO DO:
-- expand this to automatically choose proper observing blocks for each moon
-    in order to maximize SNR of the detection
-- expand this to automatically build Mab_full, Mab_block45, and Mab_block67
+- expand this to automatically build Mab_full, Mab_firsthalf, Mab_secondhalf
+- get optimal detections of the other moons
 '''
 
 from shift_stack_moons.shift_stack_moons import *
@@ -15,17 +14,42 @@ import pandas as pd
 from astroquery.jplhorizons import Horizons
 import paths
 
+code = 'Mab'
+band = 'K'
+perturbation_experiment = False #set this flag to True to re-build mock data in paths.data / perturbation_experiment
+
+constants_dict = {
+    'Mab':{
+        'H':{'stem':'urh', 'reverse':True, 'canny':False, 'start_idx':41, 'end_idx':64}, #urh156
+        'K':{'stem':'urk', 'reverse':True, 'canny':True, 'start_idx':0, 'end_idx':24}, #urk146
+        },
+    'Ophelia':{
+        'H':{},
+        'K':{},
+        },
+    'Cordelia':{
+        'H':{},
+        'K':{},
+        },
+    'Perdita':{
+        'H':{},
+        'K':{},
+        },
+}
+
 # find filenames
 data_dir = paths.data / 'reduced/2019oct28'
 data_files = os.listdir(data_dir)
-stem = 'urk'
+stem = constants_dict[code][band]['stem']
 obscode = '568'
-code = 'Mab'
 date = '2019-10-28'
 tstart = date+' 00:00'
 tend = date+' 23:59'
-perturbation_experiment = False #set this flag to True to re-build mock data in paths.data / perturbation_experiment
 pixscale = 0.009971
+start_idx = constants_dict[code][band]['start_idx']
+end_idx = constants_dict[code][band]['end_idx']
+reverse = constants_dict[code][band]['reverse'] #do you want to input the files backward so the moon is stacked to the last position instead of the first position?
+canny = constants_dict[code][band]['canny']
 
 outfname = paths.data / f"results/{stem}_{code}_{date}.fits"
 
@@ -40,13 +64,13 @@ block_ends = np.argwhere(diff > 1).T[0]+1
 block_starts = np.concatenate([np.array([0]), block_ends])
 block_ends = np.concatenate([block_ends, np.array([len(fnames)])])
 fnames_sorted = np.array(fnames)[sorti]
[…]

### 2023-02-06 src/tex/ms.tex
first full draft

@@
 
-\newcommand{\ergsec}{erg s$^{-1}$ cm$^{-2}$ $\mu$m$^{-1}$\ }
+\newcommand{\ergsec}{erg s$^{-1}$ cm$^{-2}$ $\mu$m$^{-1}$}
 
@@
 % Author list
-\author{@emolter}
+%\author{@emolter}
+\author{Ned}
 
@@
 We report the first near-infrared detection of Uranus's smallest known moon Mab, the presumed source of the blue and diffuse $\mu$ ring, using the NIRC2 instrument at Keck Observatory.
-something about shift-and-stack
-If the moon has an effective radius of 12 km as previously proposed based on HST data, its geometric albedo would be xx at 1.6 $\mu$m and phase angle 0.02$^\circ$, while if it has a radius of 6 km, its geometric albedo would be xx.
-Taken along with the HST albedo measurements, this implies Mab is (much fainter than / much brighter than / about the same as) expected in the near-infrared.
-We propose that this is due to ...
-(remember to talk about low phase angle and opposition surge somewhere).
+The detection was permitted by an updated shift-and-stack procedure allowing us to track Mab across the detector in 23 separate exposures taken over $\sim$2 hours, as well as the very low (0.02$^\circ$) phase angle at the time of observation.
+At this phase angle, Mab has an integrated I/F of $23 \pm 6$ km$^{2}$ at 1.6 $\mu$m and $35 \pm 9$ km$^{2}$ at 2.1 $\mu$m. 
+Comparing these values with Mab's visible reflectance as derived by HST reveals that Mab is spectrally blue; its (0.5 $\mu$m)/(1.6 $\mu$m) color is more consistent with Miranda's value than Puck's value.
+We therefore propose that Mab is more likely a $\sim$6-km radius body with a Miranda-like surface than a 12-km radius body with a Puck-like surface, but we caution that a Puck-like color is only ruled out at the 2$\sigma$ level.
 We also report (the first?) infrared photometry of Ophelia, (Cordelia?), and Perdita.
@@
 
-something about the circumplanetary environment of Uranus
-
 % does the below text fit in anywhere?
@@
 Material transport is important for understanding the surfaces of Miranda, Puck, and the smaller inner moons, too, but these processes are less well-studied.
-Puck's leading hemisphere has a significantly bluer spectral slope than its trailing hemisphere, meaning that it may be sweeping up material from the $\mu$ ring \citep{french17}, but this has not been confirmed.
+Puck's leading hemisphere has a significantly bluer spectral slope than its trailing hemisphere, meaning that it may be sweeping up material from the $\mu$ ring \citep{french17}.
 %this is a DPS abstract - is there a better reference?
@@
 Those authors propose three possible sources of the regolith material: deposition from the $\mu$ ring, plume deposits from a subsurface ocean, and/or giant impact ejecta.
-One sentence here linking these paragraphs
 
-Uranus's tiny moon Mab is embedded in the faint, diffuse $\mu$ ring, the only ring in the solar system with a blue spectrum other than Saturn's E ring, which is sourced from Enceladus's cryovolcanism \citep{depater06}.
+The faint, diffuse $\mu$ ring is therefore crucial for understanding the evolution of Uranus's circumplanetary system as a whole, but its properties and origin remain poorly understood.
+It is the only ring in the solar system with a blue spectrum other than Saturn's E ring, which is sourced from Enceladus's cryovolcanism \citep{depater06}.
 The E~ring is blue due to its abundance of tiny ($\lesssim$1 $\mu$m) particles and paucity of larger grains \citep{showalter91, depater04, hillier07}.
-While active cryovolcanism on such a small body as Mab seems highly unlikely, alternative theories for the formation and maintenance of the $\mu$ ring remain unconstrained by data.
-Mab has been proposed to be outbursting like the active Centaur Echeclus, with the blue color of the $\mu$ ring attributable not to small particle sizes but to a high abundance of carbon-rich organic matter \citep{seccull19}.
+The tiny moon Mab is embedded in, and is the presumed source of, the $\mu$ ring, but active cryovolcanism on such a small body seems highly unlikely.
+Instead, it has been proposed that Mab outbursts like the active Centaur Echeclus, with the blue color of the $\mu$ ring attributable not to small particle sizes but to a high abundance of carbon-rich organic matter \citep{seccull19}.
 Alternatively, interplanetary dust and/or charged plasma impacting Mab's surface may liberate enough particles to form the $\mu$ ring.
@@
 
-The radius and albedo of Mab remain under debate.
-Based on HST observations, \citet{showalter06} proposed two end-member cases: Mab has a $\sim$6 km radius with a Miranda-like icy surface and an albedo of $\sim$0.46; or Mab has a $\sim$12 km radius and an albedo of $\sim$0.1, indicating the presence of dark organic compounds on its surface like its other nearest neighbor, Puck.
-However, a sensitive near-infrared search with Keck did not detect the moon, leading to the proposal that Mab's radius is $\lesssim$6 km and as dark at wavelengths from 1.6-2.4 $\mu$m as Uranus's inner main rings \citep[albedo $\sim$0.05;][]{paradis19, paradis23}.
+The HST observations that discovered Mab could not uniquely constrain its radius and albedo, which are degenerate with respect to the reflected flux of an unresolved body \citep{showalter06}.
+Those authors proposed two end-member cases: Mab has a $\sim$6 km radius with a Miranda-like icy surface and an albedo of $\sim$0.46; or Mab has a $\sim$12 km radius and an albedo of $\sim$0.1, indicating the presence of dark organic compounds on its surface like its other nearest neighbor, Puck.
+A previous near-infrared search with Keck did not detect the moon, leading to the proposal that Mab's radius is $\lesssim$6 km and as dark at wavelengths from 1.6-2.4 $\mu$m as Puck \citep[albedo $\lesssim$0.11;][]{paradis19, paradis23}.
 Strong near-IR absorption from water ice could partially account for this darkening; however, the decrease in brightness is not expected to exceed 50\% even for a very icy body \citep[c.f.
@@
 
-re-word the way Paradis is talked about above
-
 Here we present the first observations of Mab at near-infrared wavelengths.
 Our dataset and data proceessing steps are described in Section \ref{s:observations}.
-We present photometry of Mab, as well as Cordelia, Ophelia, and Perdita,
+We present photometry of Mab, as well as Cordelia, Ophelia, and Perdita, in Section \ref{s:results}, and compare Mab's derived infrared reflectance with the spectra of Miranda and Puck in Section \ref{s:discussion}.
 
@@
 
-This paper makes use of H- and K-band data taken on 28 October 2019 by the narrow camera of the NIRC2 instrument coupled to the Adaptive Optics (AO) system at Keck Observatory, using Uranus itself for wavefront sensing \citep{wizinowich00, vandam04}.
+This paper makes use of H- and Kp-band data taken on 28 October 2019 by the narrow camera of the NIRC2 instrument coupled to the Adaptive Optics (AO) system at Keck Observatory, using Uranus itself for wavefront sensing \citep{wizinowich00, vandam04}.
 The same data were analyzed by \citet{paradis23}, so we refer the reader to that paper for a detailed description of the observation and data reduction procedures.
-The standard star was FS2 from the UKIRT Faint Standard Star list,\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc/UKIRTstds.html}} and standard photometric calibration procedures resulted in calibration constants $C_H = 8.87\times10^{-17}$ and $C_K = 9.11\times10^{-17}$ to convert from 1 count per second to 1 \ergsec.
+The standard star was FS2 from the UKIRT Faint Standard Star list,\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc/UKIRTstds.html}} and standard photometric calibration procedures resulted in calibration constants $C_H = 8.87\times10^{-17}$ and $C_K = 9.11\times10^{-17}$ to convert from 1 count per second to 1 \ergsec{}.
 The uncertainty in the photometric calibration was estimated from the spread in measured fluxes from the standard star between frames.
@@
 
-Our full dataset consisted of 23 exposures of 120 seconds each in H-band (1.6 $\mu$m) and 24 exposures of 120 seconds each in K-band (2.2 $\mu$m); these were all the frames taken on 28 October 2019 in which Mab's expected position was inside the field of view of the narrow camera; see the left panel of Figure \ref{fig:detection}.
+Our full dataset consisted of 23 exposures of 120 seconds each in H-band (1.6 $\mu$m) and 24 exposures of 120 seconds each in Kp-band (2.1 $\mu$m); these were all the frames taken on 28 October 2019 in which Mab's expected position was inside the field of view of the narrow camera (Figure \ref{fig:detection}, left panel).
 The proper motion of Mab is roughly 30 mas (3 pixels) per minute, which means that each frame had to be shifted relative to the previous one in accordance with Mab's expected vector of motion to improve the signal-to-noise ratio (SNR).
 This so-called ``shift-and-stack" technique has been used by other authors to improve the SNR of moving point sources, including to measure photometry of other small moons of Uranus with NIRC2 \citep[][]{paradis19, paradis23}.
-Our shift-and-stack procedure differs in several ways from the one implemented by those authors, though, and we describe it fully in Appendix \ref{s:shiftandstack}.
-The application of shift-and-stack resulted in one stacked image per filter at the expected position of Mab, representing effective integration times of 2760 seconds in H-band and 2880 seconds in K-band.
+Our shift-and-stack procedure differs in several ways from the one implemented by those authors, and we describe it fully in Appendix \ref{s:shiftandstack}.
+The application of shift-and-stack resulted in one stacked image per filter at the expected position of Mab, representing effective integration times of 2760 seconds in H-band and 2880 seconds in Kp-band.
 
@@
 \includegraphics[width=0.5\textwidth]{figures/detection_images_Mab.png}
-\caption{\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected position of Mab in each of our 23 H-band exposures.
+\caption{\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected position of Mab in each of our 23 H-band and 24 Kp-band exposures.
 The bright and faint point sources visible in the image are Miranda and Puck, respectively.
-\textbf{Right:} Detection of Mab in H-band (top panel) and tentative detection in K-band (bottom panel) using the shift-and-stack technique.\label{fig:detection}}
+\textbf{Right:} Detection of Mab in H-band (top panel) and tentative detection in Kp-band (bottom panel) using the shift-and-stack technique.\label{fig:detection}}
 \end{figure}
@@
 An image of our H-band detection of Mab is shown in the upper right panel of Figure \ref{fig:detection}.
-The moon appears slightly vertically extended because its proper motion was roughly 6 pixels per 120-second frame, moving approximately toward sky North.
 The detection is in a low-SNR regime, but we are confident that it is real for three reasons.
@@
 In short, we added random offsets to the expected position of Mab in each frame, then carried out shift-and-stack in the same way as we did for the true expected position.
-We repeated this procedure with different random offsets 100 times, and found that no noise spikes as bright as our Mab detection appeared anywhere in any of these 100 different stacks; see Appendix \ref{s:falsepositives} for more details.
+We repeated this procedure with different random offsets 100 times, and found that no noise spikes as bright as our Mab detection appeared anywhere in any of those 100 stacks; see Appendix \ref{s:falsepositives} for more details.
 
@@
 We therefore determined the flux of Mab using a flux bootstrapping procedure similar to that applied to Keck-observed point sources by many other authors \citep[e.g.,][]{gibbard05, molter19, paradis23}, the specifics of which we summarize in Appendix \ref{s:bootstrapping}.
-We find the total flux of Mab to be $(5.2 \pm 1.7)\times10^{-16}$ \ergsec in H-band, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the flux bootstrapping error (see Appendix \ref{s:bootstrapping}) and the 20\% photometric calibration error.
-This flux level corresponds to an integrated I/F of XX km$^2$ at 1.6 $\mu$m, where the integrated I/F is defined as the sky-projected area the moon would have if it were a perfect Lambertian reflector \citep[i.e., a geometric albedo of unity][]{karkoschka01}.
-Note that the Sun-target-observer phase angle of these observations was only 0.02$^\circ$, so the opposition effect was likely substantial, as discussed more in Section \ref{s:discussion}.
+We find the total flux of Mab to be $(5.9 \pm 1.4)\times10^{-16}$ \ergsec{} in H-band, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the flux bootstrapping error and the 20\% photometric calibration error.
+This flux level corresponds to an integrated I/F of $23 \pm 6$ km$^{2}$ at 1.6 $\mu$m, where the integrated I/F is defined as the sky-projected area the moon would have if it were a perfect Lambertian reflector \citep[i.e., a geometric albedo of unity;][]{karkoschka01}.
+Note that the Sun-target-observer phase angle $\alpha$ of these observations was only 0.02$^\circ$, so the opposition surge was likely substantial, as discussed more in Section \ref{s:discussion}.
+The sub-solar longitude of Mab passed through 270$^\circ$ during the $\sim$2 hours of observations and the sub-observer latitude was 46$^\circ$, so the reflectance values we report represent an average of the leading and trailing hemispheres.
 
@@
 The expected vector of motion of Mab is also overlain (blue arrow).
-\textbf{Right:} The same shifted-and-stacked detection image of Mab shown in the right panel of Figure \ref{fig:detection}, but zoomed out and stretched to show the apparent trajectories of Puck and Miranda.
+\textbf{Right:} The same shifted-and-stacked detection image of Mab shown in the right panel of Figure \ref{fig:detection}, but zoomed out and on a different color scale to show the apparent trajectories of Puck and Miranda.
 Mab's position is marked with a purple circle.
@@
 
-A very faint region of positive flux was observed at the expected position of Mab after stacking the K-band data (see Figure \ref{fig:detection}).
+A very faint region of positive flux was observed at the expected position of Mab after stacking the Kp-band data (see Figure \ref{fig:detection}).
 This feature is not clearly distinguishable by eye from positive noise spikes elsewhere in the frame.
 The false positive rate experiment discussed in Appendix \ref{s:falsepositives} shows that a noise spike of similar brightness would appear within $\sim$50 pixels of the expected position $\sim$8\% of the time.
-However, our uncertainty in Mab's position is roughly one H-band PSF FWHM, or $\sim$4 pixels, because we detected Mab at the expected position in H-band.
+However, our uncertainty in Mab's position is roughly one H-band PSF FWHM, or $\pm 2$ pixels, because we detected Mab at the expected position in H-band.
 We therefore label this a tentative detection.
-Photometry was performed in an identical way as for the H-band data, and we found a flux of $(3.6 \pm 0.9)\times10^{-16}$ \ergsec.
+Photometry was performed in an identical way as for the H-band data, and we found a flux of $(3.4 \pm 0.9)\times10^{-16}$ \ergsec{}.
+This corresponds to an integrated I/F of $35 \pm 9$ km$^{2}$ at 2.1 $\mu$m, again at phase angle 0.02$^\circ$.
 
@@
 
-We report the detection of Ophelia in H- and K-band and Perdita in H-band [CHECK K-BAND AGAIN].
+We report the detection of Ophelia in H- and Kp-band and Perdita in H-band [CHECK K-BAND AGAIN].
 Something about Cordelia! do we actually see it?
@@
 
-The photometric model of \citet{karkoschka01} defines the I/F of a moon as the product of four normalized functions and a constant:
-\begin{equation}
-	\label{eq:if}
-	I/F(l, \alpha, \lambda) = f_1(l) f_2(\alpha) f_3(\lambda) f_4(\lambda) (I/F)_0
-\end{equation}
-where $f_1(l)$ is the lightcurve as a function of orbital longitude $l$ with an orbital average of unity, $f_2(\alpha)$ is the phase function scaled to unity at phase angle $\alpha = 0$, $f_3(\lambda)$ is the solar spectrum (the ``continuum'') at the observed wavelength $\lambda$ scaled to unity at 550 nm, $f_4(\lambda)$ is the band/continuum ratio, used to account for wavelength-dependent absorption features in the spectrum of the moon, and $(I/F)_0$ is the reflectivity at $\alpha = 0$ and $\lambda = 550$ nm, averaged over orbital longitude.
+The infrared brightness of Mab was approximately a factor of two fainter than that observed by \citet{showalter06} with HST at 0.5 $\mu$m.
+We compare the I/F of Mab in the three available filters (HST clear, H, Kp) with I/F values in the same filters for Puck and Miranda \citep{karkoschka01, gibbard05, paradis23} in Figure \ref{fig:spectrum} assuming Mab has either a 6-km or 12-km radius.
+Ratios between these filters are compiled in Table \ref{tab:color}.
+The visible/H ratio of Mab, which has the lowest uncertainty, is within 1$\sigma$ of Miranda's visible/H ratio but $\sim$2$\sigma$ away from Puck's.
+We therefore marginally prefer the interpretation that Mab is a 6-km body with a Miranda-like water-ice-rich surface; however, the alternative interpretation that Mab is a 12-km body with a Puck-like surface rich in organic aerosols cannot be ruled out by the available data.
 
-Use the above to contextualize Showalter observations, Sam's upper limit, and the observed brightness in H-band vs K-band.
+\input{output/color_table.tex}
 
-Sam's upper limit
+\begin{figure}
+\includegraphics[width=0.7\textwidth]{figures/reflectance_spectrum.png}
+\caption{Comparison between the spectra of Mab, Miranda, and Puck.
+HST data for Puck and Miranda are from \citet{karkoschka01} ($\alpha$ = 0.034$^\circ$).
+Keck H- and Kp-band data for Miranda are from \citet{gibbard05} (rescaled from $\alpha$ = 1.9$^\circ$ to Mab's observed $\alpha$ = 0.02$^\circ$ using the \citet{karkoschka01} photometric model).
+Keck H- and Kp-band data for Puck are from \citet{paradis23} ($\alpha$ = 0.02$^\circ$).
+HST Mab data are from \citet{showalter06} ($\alpha$ = 0.08$^\circ$.)}
+\label{fig:spectrum}
+%\script{compute_if.py} % needs pip installable pylanetary...
+\end{figure}
 
-What does it say about mu ring?
+Our reported H-band flux of $(5.9 \pm 1.4)\times10^{-16}$ \ergsec{} is seemingly in tension with the 3$\sigma$ upper limit of $2.4 \times 10^{-16}$ \ergsec{} derived previously \citep[][]{paradis19}, which we have rescaled to account for updated photometric calibration constants reported in \citet{paradis23}.
+However, those observations were taken at a phase angle of $0.65^\circ$.
+If we rescale the limit to the $0.02^\circ$ phase angle of our observations according to the \citet{karkoschka01} photometric model for Miranda, the limit would be $3.2 \times 10^{-16}$ \ergsec{}, within 2$\sigma$ of our derived result and therefore statistically insignificant.
+The \citet{paradis23} requirement that Mab's H-band geometric albedo be $<0.11$ for a 6-km effective radius is disfavored by our data at the 2.0$\sigma$ level.
 
-Something perhaps about orbital stability of Mab
+%The photometric model of \citet{karkoschka01} defines the I/F of a moon as the product of four normalized functions and a constant:
+%\begin{equation}
+%	\label{eq:if}
+%	I/F(l, \alpha, \lambda) = f_1(l) f_2(\alpha) f_3(\lambda) f_4(\lambda) (I/F)_0
+%\end{equation}
+%where $f_1(l)$ is the lightcurve as a function of orbital longitude $l$ with an orbital average of unity, $f_2(\alpha)$ is the phase function scaled to unity at phase angle $\alpha = 0$, $f_3(\lambda)$ is the solar spectrum (the ``continuum'') at the observed wavelength $\lambda$ scaled to unity at 550 nm, $f_4(\lambda)$ is the band/continuum ratio, used to account for wavelength-dependent absorption features in the spectrum of the moon, and $(I/F)_0$ is the reflectivity at $\alpha = 0$ and $\lambda = 550$ nm, averaged over orbital longitude.
 
@@
 
+This study was carried out using the reproducibility software
+\href{https://github.com/showyourwork/showyourwork}{\showyourwork}
+\citep{luger21}, which leverages continuous integration to
+programmatically download the data from
+\href{https://zenodo.org/}{zenodo.org}, create the figures, and
+compile the manuscript. Each figure caption contains two links: one
+to the dataset stored on zenodo used in the corresponding figure,
+and the other to the script used to make the figure (at the commit
+corresponding to the current build of the manuscript). The git
+repository associated to this study is publicly available at
+\url{https://github.com/emolter/mab}, and the release
+v.X.X allows anyone to re-build the entire manuscript. The datasets
+are stored at \url{https://doi.org/whatever}.
+
 \end{acknowledgements}
 
+\software{
+Astropy \citep{astropy:2013, astropy:2018, astropy:2022},
+Astroquery \citep{ginsburg19},
+matplotlib \citep{matplotlib07},
+numpy \citep{numpy20},
+photutils \citep{photutils140},
+pylanetary [CITE],
+scikit-image \citep{skimage14},
+scipy \citep{scipy20},
+shift\_stack\_moons [CITE]
+}
+% other \software here!
+
 \appendix
+
+\setcounter{table}{0}
+\renewcommand{\thetable}{A\arabic{table}}
+\setcounter{figure}{0}
+\renewcommand{\thefigure}{A\arabic{figure}}
 
@@
 To improve the SNR on Mab, individual 120-second frames were shifted according to the expected position of the moon relative to Uranus and then co-added; details of this procedure are presented here.
-The accuracy of the shift-and-stack procedure depends sensitively on the rotation angle of the detector, so we corrected for the 0.26$^\circ$ angular offset between NIRC2's sky North position and true sky North before starting \citep{service16}.
+The accuracy of the shift-and-stack procedure depends sensitively on the rotation angle of the detector, so we corrected for the 0.26$^\circ$ angular offset between NIRC2's sky north position and true sky north before starting \citep{service16}.
 First, we aligned the position of Uranus in all the frames using the \texttt{chi2\_shift} function of the \texttt{Astropy}-affiliated \texttt{image\_registration} Python package\footnote{\url{https://github.com/keflavich/image_registration}}, which implements the single-step discrete Fourier transform (DFT) algorithm for efficient sub-pixel image registration \citep{guizarsicairos08}.
-In K-band, cloud features and moons are brighter than the planet's disk, so we first applied a Canny edge-detection filter using the \texttt{skimage} Python package \citep{skimage14} to enhance the rings of Uranus, then ran \texttt{chi2\_shift} on those edges.
+In Kp-band, cloud features and moons are brighter than the planet's disk, so we first applied a Canny edge-detection filter using the \texttt{skimage} Python package \citep{skimage14} to enhance the rings of Uranus, then ran \texttt{chi2\_shift} on those edges.
 This alignment method was found to produce very sharp stacked images of the rings, so we were confident that it was aligning the frames accurately.
-The implementation of this alignment step permitted us to co-add all three H-band observing blocks (and two K-band observing blocks) shown in Figure \ref{fig:detection}, between which Uranus was repositioned on the detector by tens of pixels, and is the most important difference between our procedure and that of \citet{paradis19, paradis23}.
+The implementation of this alignment step permitted us to co-add all three H-band observing blocks (and two Kp-band observing blocks) shown in Figure \ref{fig:detection}, between which Uranus was repositioned on the detector by tens of pixels.
 Second, we found the median of these planet-aligned frames and subtracted it from each frame; this step suppresses the signal of non-moving sources (in this case, the planet and rings), decreasing the effects of scattered light.
-Third, the expected offset between Mab and Uranus at the time of each exposure (we define this as the start time plus half the exposure time) was taken from JPL Horizons, accessed using the \texttt{Astroquery} Python package \citep{ginsburg19}.
-We converted the expected x,y offset from units of arcseconds to pixels assuming the pixel scale of the NIRC2 narrow camera to be 0.009971\arcsec \citep{service16} and taking the distance to Uranus from the Horizons ephemeris.
-Finally, we applied the shifts using a 2-D fast Fourier transform (FFT) sub-pixel image shift, again implemented with \texttt{image\_registration}, and summed all the frames.
+Third, the expected offset between Mab and Uranus at the time\footnote{Start time plus half the exposure time} of each exposure was taken from JPL Horizons, accessed using the \texttt{Astroquery} Python package \citep{ginsburg19}.
+We converted the expected x,y offset from units of arcseconds to pixels assuming the pixel scale of the NIRC2 narrow camera to be 0.009971\arcsec \citep{service16}.
+Finally, we applied the shifts using a 2-D fast Fourier transform (FFT) sub-pixel image shift, again implemented with \texttt{image\_registration}, and summed all the frames to produce a single stacked frame.
 
@@
 We then measured the flux inside apertures of the same size but centered on the standard star; call these $F_{\star i}$.
-Comparing $F_{\star i}$ with the true flux of the standard star $F_\star$ (as measured in a very large aperture of radius $\gtrsim$100 pixels) yielded a correction for the wings of the PSF for a given value of $r_{i}$, given by simply $C_{psf} = F_{\star i}/F_\star$.
-The flux of the background must also be subtracted in order to accurately determine $F_{M i}$; we defined the background region using a circular annulus centered on Mab with inner radius $r_i + 5$ pixels and outer radius $r_o$.
+Comparing $F_{\star i}$ with the true flux of the standard star $F_\star$ (as measured in a very large aperture of radius $\gtrsim$100 pixels) yielded a correction at a given value of $r_{i}$ given by simply $C_{psf} = F_{\star i}/F_\star$.
+The flux of the background must be subtracted in order to accurately determine $F_{M i}$; we defined the background region using a circular annulus centered on Mab with inner radius $r_i + 5$ pixels and outer radius $r_o$.
 The background flux level $F_{B o}$ was taken to be the median of pixels within the background annulus multiplied by the area of the Mab aperture $\pi r_i^2$.
 We also varied $r_o$ over a range of values to test the sensitivity of our flux estimate to the choice of background region.
-The flux of Mab $F_{i,o}$ for a given $r_i, r_o$ pair is given by $F_M = (F_{M i} - F_{B o}) / C_{psf}$, and the value of $F_{i,o}$ is displayed as a function of $r_i$ and $r_o$ in Figure \ref{fig:wing}.
-The final flux estimate of Mab is given by the mean of $F_{i,o}$ over a reasonable range of $r_i$ and $r_o$ values, and the uncertainty is given by the standard deviation of $F_{i,o}$, which is $\approx$9\%.
-(This 9\% error is multiplied in quadrature with the typical 20\% flux calibration error from standard star observations with Keck).
-We chose smaller values of $r_i$ than \citet{paradis23} because the SNR of our Mab detection is much lower than the SNR of the moon detections shown in that paper.
+The flux of Mab $F_{i,o}$ for a given $r_i, r_o$ pair is given by $F_M = (F_{M i} - F_{B o}) / C_{psf}$.
+%, and the value of $F_{i,o}$ is displayed as a function of $r_i$ and $r_o$ in Figure \ref{fig:wing}. 
+The final flux estimate of Mab is given by the mean of $F_{i,o}$ over a reasonable range of $r_i$ and $r_o$ values, which we take to be 6-10 pixels and 15-50 pixels, respectively.
+The uncertainty is given by the standard deviation of $F_{i,o}$, which was $\approx$15\% in both H- and Kp-band.
+This error was multiplied in quadrature with the typical 20\% flux calibration error from standard star observations with Keck.
 
-\begin{figure}
-\includegraphics[width=0.3\textwidth]{figures/example_aperture.png}
-\includegraphics[width=0.7\textwidth]{figures/photometry_vs_region.png}
-\caption{\textbf{Left:} Example aperture (solid blue line) and background annulus (dot-dashed red line) centered on Mab.
+%\begin{figure}
+%\includegraphics[width=0.3\textwidth]{figures/example_aperture.png}
+%\includegraphics[width=0.7\textwidth]{figures/photometry_vs_region.png}
+%\caption{\textbf{Left:} Example aperture (solid blue line) and background annulus (dot-dashed red line) centered on Mab.
 The values of $r_i$ and $r_o$ in this example are 7 and 45 pixels, respectively.
 \textbf{Right:} Derived flux of Mab as a function of $r_i$ and $r_o$.\label{fig:wing}}
-\end{figure}
+%\end{figure}
 
@@
 
-Our detection of Mab has a low SNR, and the moon was located in the lower-left quadrant of the NIRC2 NARROW camera, which is known to have non-Gaussianity in its noise statistics,\footnote{https://www2.keck.hawaii.edu/inst/nirc2/ObserversManual.html} including vertical stripes of correlated noise.
-It is therefore natural to wonder whether the shift-and-stack technique is somehow injecting false positives by stacking noise spikes atop one another.
-To test whether this is the case, we performed an experiment to test the false positive rate within the true detector noise and scattered light environment of the data, as follows.
+Mab was observed in the lower-left quadrant of the NIRC2 NARROW camera, which is known to have non-Gaussianity in its noise statistics,\footnote{https://www2.keck.hawaii.edu/inst/nirc2/ObserversManual.html} including vertical stripes of correlated noise.
+Given the low SNR of the detection, it is natural to wonder whether the shift-and-stack technique is injecting false positives by stacking noise spikes atop one another.
+To test whether this is the case, we performed an experiment to test the false positive rate within the same detector noise and scattered light environment of the data, as follows.
 The expected position of Mab was shifted by a random x,y offset of mean amplitude 20 pixels in each frame, then the shift-and-stack algorithm was re-run assuming these new randomly-selected shifts and the output frame was saved.
 This experiment was repeated 100 times with different random offsets applied.
-We then searched for point sources in these 100 test stacks by applying a center-surround (difference-of-Gaussains) filter with an FWHM of 4 pixels for the inner Gaussian\footnote{this corresponds roughly to the diffraction-limited beam size of Keck in H-band} and an FWHM of 12 pixels for the outer Gaussian.
+We then searched for point sources in these 100 test stacks by applying a center-surround (difference-of-Gaussians) filter with an FWHM of 4 pixels for the inner Gaussian\footnote{This corresponds roughly to the diffraction-limited beam size of Keck in H-band.} and an FWHM of 12 pixels for the outer Gaussian.
 The center-surround filter is the appropriate choice because it accentuates features at the desired spatial frequency and downweights low spatial frequency features.
 The visual systems of humans and other animals employ center-surround antagonism \citep{graham06}, so this technique is a reasonable proxy for ``by-eye'' detection.
-We then binned the filtered images by a factor of 2 in each direction.
+We binned the filtered images by a factor of 2 in each direction.
 Finally, we computed the amplitude of the brightest pixel in each binned frame in units of the RMS noise of the input image.
@@
 The detection of Mab in the real data was found to have a higher SNR than any peak in any of the 100 test frames in H-band (see Figure \ref{fig:randomstack}).
-In K-band, we find that a noise spike with an amplitude higher than our tentative detection is present in 8 out of 100 frames (Figure \ref{fig:randomstack_K}).
-However, because our tentative detection is in the correct position on the detector relative to Miranda and Puck, we feel justified in labeling it a tentative detection rather than a non-detection and extracting photometry.
+In Kp-band, we find that a noise spike with an amplitude higher than our tentative detection is present in 8 out of 100 frames (Figure \ref{fig:randomstack_K}).
+However, because our tentative detection is in the correct position on the detector relative to Miranda and Puck, we feel justified in labeling it a tentative detection rather than a non-detection.
 We tested other choices of inner and outer FWHM for the center-surround filter and different amounts of binning, and found that the results remained similar within reasonable ranges of these parameters.
@@
 \includegraphics[width=1.0\textwidth]{figures/random_stack_experiment_Mab_K.png}
-\caption{Results of the false positive rate experiment for K band. See caption of Figure \ref{fig:randomstack} for a description. \label{fig:randomstack_K}}
+\caption{Results of the false positive rate experiment for Kp band. See caption of Figure \ref{fig:randomstack} for a description. \label{fig:randomstack_K}}
 \end{figure}

### 2023-02-06 src/scripts/compute_if.py

@@ -2,19 +2,32 @@
 
 import numpy as np
 import matplotlib.pyplot as plt
+from pylanetary.utils import *
+from astroquery.jplhorizons import Horizons
+from astropy.io import ascii
+from astropy import table
+import paths
 
 '''
 Start with the best photometry of a moon in erg s-1 cm-1 um-1 units,
 determine the integrated I/F,
-determine the I/F for some assumed radii, like 6 km and 12 km
+plot this against the Showalter value for integrated I/F
 
-use the Jupyter notebooks from the JWST proposal for help
+description of types of albedo: https://the-moon.us/wiki/Albedo
+
+to do:
+find a smart place to put H and K band bandpass data within the showyourwork architecture
 '''
 
+caption = r'Available color information on Mab compared with its nearest orbital neighbors, Puck and Miranda. See Figure \ref{fig:spectrum} caption for data sources. \label{tab:color}'
+
+code = 'Mab'
+band = 'K'
+keck_transmission_dir = '/Users/emolter/Python/nirc2_reduce/filter_passbands/'
 constants_dict = {
     'Mab':{
-        'H':{'flux':5.2e-16, 'err':1.7e-16, }, 
-        'K':{'flux':3.6e-16, 'err':0.9e-16, }, 
+        'H':{'flux':5.9e-16, 'flux_err':1.4e-16, 'bp_file':keck_transmission_dir + 'h.csv'}, 
+        'K':{'flux':3.4e-16, 'flux_err':0.9e-16, 'bp_file':keck_transmission_dir + 'kp.csv'}, 
         },
     'Ophelia':{
         'H':{},
@@ -29,3 +42,138 @@ constants_dict = {
         'K':{},
         },
 }
+
+# get sun-target and Earth-target distance from Horizons
+obscode = '568'
+date = '2019-10-28'
+tstart = date+' 11:00' #this just needs to be approximate
+tend = date+' 12:00'
+horizons_obj = Horizons(
+    id=code,
+    location=obscode,
+    epochs={"start": tstart, "stop": tend, "step": "1h"},
+)
+ephem = horizons_obj.ephemerides()[0]
+target_sun_dist = ephem['r']
+target_obs_dist = ephem['delta']
[…]

### 2023-02-06 src/scripts/photometry.py

@@ -43,6 +43,13 @@ photometry_constants_dict = {
 }
 
 
+## compute the photometry for many inner and outer radii
+nsamples = 50
+ri0 = 5
+ri1 = 10
+ro0 = ri1 + 5
+ro1 = 50
+
 stem = photometry_constants_dict[code][band]['stem']
 n_coadds_raw = photometry_constants_dict[code][band]['coadds'] #apparently the "raw" images were already divided by the number of coadds so this is needed
 xpos = photometry_constants_dict[code][band]['xpos'] 
@@ -51,10 +58,6 @@ ypos = photometry_constants_dict[code][band]['ypos']
 C1 = photometry_constants_dict[code][band]['C1']  # from cts s-1 to erg s-1 cm-2 um-1; see Paradis+23 Section 2.5.1
 
 fname = paths.data / f'results/{stem}_{code}_2019-10-28.fits'
-boxr = 50
-rinner = 7
-rmid = 12
-router = 45
 CU, CR = 1,1 # see Paradis+23 Section 2.5. this could be looked at later but for now it's ok
 
 
@@ -77,7 +80,12 @@ def get_wing_corr(r, wing_corrs):
     corr2 = wing_corrs["2"](r)
     return np.mean(np.array([corr0, corr1, corr2]))
 
+'''
 # compute the photometry for a single inner and outer radius
+boxr = 50
+rinner = 7
+rmid = 12
+router = 45
 ap = aperture.CircularAperture((xpos,ypos), r=rinner)
 ann = aperture.CircularAnnulus((xpos,ypos), r_in=rmid, r_out=router)
 apstats = aperture.ApertureStats(data, ap)
@@ -90,7 +98,6 @@ corrected_flux = (C1/itime) * (flux / wing_correction)
 #print(f'Corrected total flux = {corrected_flux} erg s-1 cm-2 um-1')
 rms = annstats.std * np.sqrt(ap.area)
 print(f'Approximate SNR = {flux / rms}')
-
 
 # plot
 doplot = True
@@ -107,14 +114,7 @@ if doplot:
     plt.savefig(paths.figures / f"example_aperture_{code}_{stem}.png", dpi=300)
     plt.show()
     plt.close()
-
-
-## compute the photometry for many inner and outer radii
-nsamples = 50
-ri0 = 5
-ri1 = 12
-ro0 = ri1 + 5
-ro1 = 50
+'''
 
[…]

### 2023-02-06 src/tex/ms.tex
made build work with snakefile

@@
 %\author{@emolter}
-\author{Ned}
+\author[0000-0003-3799-9033]{Edward M. Molter}
+\affiliation{Earth and Planetary Science Department, University of California, Berkeley, CA 94720, USA}
+\correspondingauthor{Edward M. Molter}
+\email{emolter@berkeley.edu}
 
-\author{Imke}
+\author{Imke de Pater}
+\affiliation{Earth and Planetary Science Department, University of California, Berkeley, CA 94720, USA}
 
-\author{Chris}
+\author{Chris Moeckel}
+\affiliation{Earth and Planetary Science Department, University of California, Berkeley, CA 94720, USA}
 
@@
 The detection was permitted by an updated shift-and-stack procedure allowing us to track Mab across the detector in 23 separate exposures taken over $\sim$2 hours, as well as the very low (0.02$^\circ$) phase angle at the time of observation.
-At this phase angle, Mab has an integrated I/F of $23 \pm 6$ km$^{2}$ at 1.6 $\mu$m and $35 \pm 9$ km$^{2}$ at 2.1 $\mu$m. 
+At this phase angle, Mab has an integrated I/F of 
+\variable{output/Mab_urh_intif.txt} $\pm$ \variable{output/Mab_urh_intiferr.txt} km$^{2}$ 
+at 1.6 $\mu$m and 
+\variable{output/Mab_urk_intif.txt} $\pm$ \variable{output/Mab_urk_intiferr.txt} km$^{2}$ 
+at 2.1 $\mu$m. 
 Comparing these values with Mab's visible reflectance as derived by HST reveals that Mab is spectrally blue; its (0.5 $\mu$m)/(1.6 $\mu$m) color is more consistent with Miranda's value than Puck's value.
@@
 \end{abstract}
+
+\keywords{}
 
@@
 % does the below text fit in anywhere?
-The small regular moons comprising the Portia group in the Uranian system represent the most densely-packed set of satellites known, with semimajor axis separations of 3\% on average \citep{showalter20}; as such, the system is predicted to be chaotic, with collisions occurring on 10$^5$-10$^7$-year timescales \citep{duncan97, french12}.
+The small regular moons comprising the Portia group in the Uranian system represent the most densely-packed set of satellites known, with semimajor axis separations of 3\% on average \citep{showalter20}; as such, the system is predicted to be chaotic, with collisions occurring on 10$^5$- to 10$^7$-year timescales \citep{duncan97, french12}.
 Indeed, the faint dusty $\nu$ ring, situated between the orbits of Portia and Rosalind, has been proposed to be the remnant of such a collision.
@@
 We therefore determined the flux of Mab using a flux bootstrapping procedure similar to that applied to Keck-observed point sources by many other authors \citep[e.g.,][]{gibbard05, molter19, paradis23}, the specifics of which we summarize in Appendix \ref{s:bootstrapping}.
-We find the total flux of Mab to be $(5.9 \pm 1.4)\times10^{-16}$ \ergsec{} in H-band, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the flux bootstrapping error and the 20\% photometric calibration error.
-This flux level corresponds to an integrated I/F of $23 \pm 6$ km$^{2}$ at 1.6 $\mu$m, where the integrated I/F is defined as the sky-projected area the moon would have if it were a perfect Lambertian reflector \citep[i.e., a geometric albedo of unity;][]{karkoschka01}.
+We find the total flux of Mab to be
+(\variable{output/Mab_urh_flux.txt} $\pm$ \variable{output/Mab_urh_fluxerr.txt})$\times10^{-16}$ \ergsec{} 
+in H-band, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the flux bootstrapping error and the 20\% photometric calibration error.
+This flux level corresponds to an integrated I/F of
+\variable{output/Mab_urh_intif.txt} $\pm$ \variable{output/Mab_urh_intiferr.txt} km$^{2}$ 
+at 1.6 $\mu$m, where the integrated I/F is defined as the sky-projected area the moon would have if it were a perfect Lambertian reflector \citep[i.e., a geometric albedo of unity;][]{karkoschka01}.
 Note that the Sun-target-observer phase angle $\alpha$ of these observations was only 0.02$^\circ$, so the opposition surge was likely substantial, as discussed more in Section \ref{s:discussion}.
@@
 The expected motion of Puck and Miranda relative to Mab are plotted as red and orange lines, respectively.
-Miranda is still overexposed in this image stretch, so the brightest pixels in Miranda's track are highlighted in cyan.\label{fig:astrometry}}
+Miranda is still overexposed in this image stretch, so the brightest pixels in Miranda's track are highlighted in cyan.}
+\label{fig:astrometry}
+\script{relative_position_miranda_puck.py}
 \end{figure}
@@
 This feature is not clearly distinguishable by eye from positive noise spikes elsewhere in the frame.
-The false positive rate experiment discussed in Appendix \ref{s:falsepositives} shows that a noise spike of similar brightness would appear within $\sim$50 pixels of the expected position $\sim$8\% of the time.
+The false positive rate experiment discussed in Appendix \ref{s:falsepositives} shows that a noise spike of similar brightness would appear within $\sim$50 pixels of the expected position $\sim$\variable{output/perturbation_percent_higher_K.txt}\% of the time.
 However, our uncertainty in Mab's position is roughly one H-band PSF FWHM, or $\pm 2$ pixels, because we detected Mab at the expected position in H-band.
 We therefore label this a tentative detection.
-Photometry was performed in an identical way as for the H-band data, and we found a flux of $(3.4 \pm 0.9)\times10^{-16}$ \ergsec{}.
-This corresponds to an integrated I/F of $35 \pm 9$ km$^{2}$ at 2.1 $\mu$m, again at phase angle 0.02$^\circ$.
+Photometry was performed in an identical way as for the H-band data, and we found a flux of
+(\variable{output/Mab_urk_flux.txt} $\pm$ \variable{output/Mab_urk_fluxerr.txt})$\times10^{-16}$ \ergsec{} 
+. This corresponds to an integrated I/F of 
+\variable{output/Mab_urk_intif.txt} $\pm$ \variable{output/Mab_urk_intiferr.txt} km$^{2}$ 
+at 2.1 $\mu$m, again at phase angle 0.02$^\circ$.
 
@@
 
-\input{output/color_table.tex}
+\variable{output/color_table.tex}
 
@@
 \label{fig:spectrum}
-%\script{compute_if.py} % needs pip installable pylanetary...
+\script{compute_if.py}
 \end{figure}
 
-Our reported H-band flux of $(5.9 \pm 1.4)\times10^{-16}$ \ergsec{} is seemingly in tension with the 3$\sigma$ upper limit of $2.4 \times 10^{-16}$ \ergsec{} derived previously \citep[][]{paradis19}, which we have rescaled to account for updated photometric calibration constants reported in \citet{paradis23}.
+Our reported H-band flux of 
+(\variable{output/Mab_urh_flux.txt} $\pm$ \variable{output/Mab_urh_fluxerr.txt})$\times10^{-16}$ \ergsec{} 
+is seemingly in tension with the 3$\sigma$ upper limit of $2.4 \times 10^{-16}$ \ergsec{} derived previously \citep[][]{paradis19}, which we have rescaled to account for updated photometric calibration constants reported in \citet{paradis23}.
 However, those observations were taken at a phase angle of $0.65^\circ$.
@@
 photutils \citep{photutils140},
-pylanetary [CITE],
+pylanetary \citep{pylanetary23},
 scikit-image \citep{skimage14},
 scipy \citep{scipy20},
-shift\_stack\_moons [CITE]
+shift\_stack\_moons \cite{shift_stack_moons23}
 }
@@
 
+\facility{Keck:II}
+
 \appendix
 
-\setcounter{table}{0}
-\renewcommand{\thetable}{A\arabic{table}}
-\setcounter{figure}{0}
-\renewcommand{\thefigure}{A\arabic{figure}}
+\restartappendixnumbering
 
@@
 Finally, we applied the shifts using a 2-D fast Fourier transform (FFT) sub-pixel image shift, again implemented with \texttt{image\_registration}, and summed all the frames to produce a single stacked frame.
+Our shift-and-stack code is publicly available on GitHub \citep{molter23}.
 
@@
 \textbf{(c)} Example filtered and binned randomized stack.
-\textbf{(d)} Histogram of the SNR of the brightest pixel in the filtered and binned test frames; the real data are demarcated with a black dashed line.\label{fig:randomstack}}
+\textbf{(d)} Histogram of the SNR of the brightest pixel in the filtered and binned test frames; the real data are demarcated with a black dashed line.}
+\label{fig:randomstack}
+\script{plot_perturbation_experiment.py}
 \end{figure}
@@
 \includegraphics[width=1.0\textwidth]{figures/random_stack_experiment_Mab_K.png}
-\caption{Results of the false positive rate experiment for Kp band. See caption of Figure \ref{fig:randomstack} for a description. \label{fig:randomstack_K}}
+\caption{Results of the false positive rate experiment for Kp band. See caption of Figure \ref{fig:randomstack} for a description. }
+\label{fig:randomstack_K}
+\script{plot_perturbation_experiment.py}
 \end{figure}

### 2023-02-06 src/scripts/compute_if.py

@@ -15,19 +15,16 @@ plot this against the Showalter value for integrated I/F
 
 description of types of albedo: https://the-moon.us/wiki/Albedo
 
-to do:
-find a smart place to put H and K band bandpass data within the showyourwork architecture
+To do: make work for the other moons, put them in the paper too
 '''
 
 caption = r'Available color information on Mab compared with its nearest orbital neighbors, Puck and Miranda. See Figure \ref{fig:spectrum} caption for data sources. \label{tab:color}'
 
 code = 'Mab'
-band = 'K'
-keck_transmission_dir = '/Users/emolter/Python/nirc2_reduce/filter_passbands/'
 constants_dict = {
     'Mab':{
-        'H':{'flux':5.9e-16, 'flux_err':1.4e-16, 'bp_file':keck_transmission_dir + 'h.csv'}, 
-        'K':{'flux':3.4e-16, 'flux_err':0.9e-16, 'bp_file':keck_transmission_dir + 'kp.csv'}, 
+        'H':{'stem':'urh', 'bp_file':paths.static / 'h.csv'}, 
+        'K':{'stem':'urk', 'bp_file':paths.static / 'kp.csv'}, 
         },
     'Ophelia':{
         'H':{},
@@ -61,8 +58,11 @@ target_omega = 1*u.km**2 / (((target_obs_dist*u.au).to(u.km))**2) #setting area 
 wls, fluxes, errs = [], [], []
 for band in ['H', 'K']:
     # get Keck filter transmission
-    flux = constants_dict[code][band]['flux'] # erg s-1 cm-2 um-1
-    flux_err = constants_dict[code][band]['flux_err'] # erg s-1 cm-2 um-1
+    stem = constants_dict[code][band]['stem']
+    with open(paths.output / f'{code}_{stem}_flux.txt', 'r') as f:
+        flux = float(f.readline()) * 1e-16 # erg s-1 cm-2 um-1
+    with open(paths.output / f'{code}_{stem}_fluxerr.txt', 'r') as f:
+        flux_err = float(f.readline()) * 1e-16 # erg s-1 cm-2 um-1
     bp_file = constants_dict[code][band]['bp_file']
     wl, trans = np.genfromtxt(bp_file, skip_header=1, delimiter=',', usecols=(0,1)).T
     wl = wl[~np.isnan(wl)][:-1] * u.micron
[…]

### 2023-02-06 src/scripts/detection_pretty_picture.py

@@ -21,7 +21,7 @@ and direction of Mab's motion across the detector during a single 2-minute expos
 The average motion of Mab over a single 2-minute exposure, projected onto the detector plane,
 is $\approx$6.2 pixels in the sky-North-Northeast direction. 
 This is larger than Keck's diffraction-limited resolution of 40 mas (4 pixels) at 1.6 $\mu$m,
-so smearing is substantial in the N-S direction, as seen in Figure \ref{fig:detection}.
+so smearing is substantial in the N-S direction
 "
 
 ready to ship!
@@ -91,7 +91,8 @@ for i, band in enumerate(['H', 'K']):
 #ax0.legend()
 plt.tight_layout()
 fig.savefig(paths.figures / f'detection_images_{code}.png', bbox=None)
-plt.show()
+#plt.show()
+plt.close()
 
 '''
 # test if noise is biased in one direction or the other to make Chris happy

### 2023-02-06 src/scripts/mab_path_on_detector.py

@@ -169,6 +169,6 @@ ax.legend()
 
 plt.tight_layout()
 fig.savefig(paths.figures / f"motion_on_detector.png", dpi=300)
-plt.show()
+#plt.show()
 plt.close()
 

### 2023-02-06 src/scripts/perturbation_experiment.py

@@ -1,150 +1,0 @@
-#!/usr/bin/env python
-
-'''
-Compile the results of the perturbation experiment
-Show that the shift-and-stack technique does not introduce spurious sources
-    Show that the perturbed frames have a similar noise level, but no sources
-        at the same SNR
-    Automate this most likely by smoothing to the Keck beam size. 
-        This inflates the single-pixel strength of Mab
-        in the real frame while decreasing the strength of any noise spikes
-Making the frames was done at the bottom of shift_stack_uranus.py
-
-"The expected position of Mab was shifted by a random x,y offset 
-    of mean amplitude 20 pixels in each frame, then the shift-and-stack algorithm was re-run
-    assuming these new randomly-selected shifts, and the output frame saved. 
-    This experiment was repeated 100 times with different random offsets applied. 
-    We then searched for point sources in these 100 test frames 
-    by applying a center-surround filter with an FWHM of 1.5 pixels\footnote{this corresponds
-    roughly to the diffraction-limited beam size of Keck in H-band}, then binned the filtered
-    images by a factor of 2 in each direction. Finally, we computed the amplitude 
-    of the brightest pixel in each binned frame in units of the RMS noise of the input image; 
-    this yielded a rough estimate of the signal-to-noise ratio of that peak. 
-    Identical filtering, binning, and SNR calculations were run on the real data. 
-    The detection of Mab in the real data was found to have a higher SNR than any peak 
-    in any of the 100 test frames; see Figure \ref{fig:randomstack}."
-
-To do:
-make it do both filters in a loop in order to make both figs that go in the paper
-but otherwise it's ready to ship
-'''
-
-import numpy as np
-import matplotlib.pyplot as plt
-from astropy.io import fits
-from pylanetary.utils import rebin
-from scipy.ndimage import gaussian_filter
-from scipy.signal import medfilt2d, convolve2d
-import paths
-from skimage.filters import difference_of_gaussians
-
-code = 'Mab'
-band = 'H'
-
[…]

### 2023-02-06 src/scripts/photometry.py

@@ -20,8 +20,6 @@ from astropy import table
 import paths
 from scipy.interpolate import interp1d
 
-code = 'Mab'
-band = 'H'
 
 photometry_constants_dict = {
     'Mab':{
@@ -42,6 +40,13 @@ photometry_constants_dict = {
         },
 }
 
+def get_wing_corr(r, wing_corrs):
+    '''wing_corrs is a dictionary defined above'''
+    corr0 = wing_corrs["0"](r)
+    corr1 = wing_corrs["1"](r)
+    corr2 = wing_corrs["2"](r)
+    return np.mean(np.array([corr0, corr1, corr2]))
+
 
 ## compute the photometry for many inner and outer radii
 nsamples = 50
@@ -50,113 +55,115 @@ ri1 = 10
 ro0 = ri1 + 5
 ro1 = 50
 
-stem = photometry_constants_dict[code][band]['stem']
-n_coadds_raw = photometry_constants_dict[code][band]['coadds'] #apparently the "raw" images were already divided by the number of coadds so this is needed
-xpos = photometry_constants_dict[code][band]['xpos'] 
-ypos = photometry_constants_dict[code][band]['ypos'] 
-# Paradis et al conversion factors for 2019-10-28
-C1 = photometry_constants_dict[code][band]['C1']  # from cts s-1 to erg s-1 cm-2 um-1; see Paradis+23 Section 2.5.1
-
-fname = paths.data / f'results/{stem}_{code}_2019-10-28.fits'
-CU, CR = 1,1 # see Paradis+23 Section 2.5. this could be looked at later but for now it's ok
-
-
-
-hdul = fits.open(fname)
-itime = hdul[0].header['ITIME']/n_coadds_raw #seconds
-data = hdul[0].data
-
-# find the wing correction by importing tables from psf_wing_correction.py
-wing_corrs = {}
-for i in [0,1,2]:
-    wing_corr_table = ascii.read(paths.data / f"tables/wing_correction_{band.upper()}_{i}.csv")
-    wing_corr_interp = interp1d(wing_corr_table['Radius'], wing_corr_table['Correction'])
-    wing_corrs[f"{i}"] = wing_corr_interp
-
-def get_wing_corr(r, wing_corrs):
-    '''wing_corrs is a dictionary defined above'''
-    corr0 = wing_corrs["0"](r)
-    corr1 = wing_corrs["1"](r)
-    corr2 = wing_corrs["2"](r)
[…]

### 2023-02-06 src/scripts/plot_perturbation_experiment.py

@@ -1,0 +1,141 @@
+#!/usr/bin/env python
+
+'''
+Compile the results of the perturbation experiment
+Show that the shift-and-stack technique does not introduce spurious sources
+    Show that the perturbed frames have a similar noise level, but no sources
+        at the same SNR
+    Automate this most likely by smoothing to the Keck beam size. 
+        This inflates the single-pixel strength of Mab
+        in the real frame while decreasing the strength of any noise spikes
+Making the frames was done at the bottom of shift_stack_uranus.py
+
+"The expected position of Mab was shifted by a random x,y offset 
+    of mean amplitude 20 pixels in each frame, then the shift-and-stack algorithm was re-run
+    assuming these new randomly-selected shifts, and the output frame saved. 
+    This experiment was repeated 100 times with different random offsets applied. 
+    We then searched for point sources in these 100 test frames 
+    by applying a center-surround filter with an FWHM of 1.5 pixels\footnote{this corresponds
+    roughly to the diffraction-limited beam size of Keck in H-band}, then binned the filtered
+    images by a factor of 2 in each direction. Finally, we computed the amplitude 
+    of the brightest pixel in each binned frame in units of the RMS noise of the input image; 
+    this yielded a rough estimate of the signal-to-noise ratio of that peak. 
+    Identical filtering, binning, and SNR calculations were run on the real data. 
+    The detection of Mab in the real data was found to have a higher SNR than any peak 
+    in any of the 100 test frames; see Figure \ref{fig:randomstack}."
+
+To do:
+make it do both filters in a loop in order to make both figs that go in the paper
+but otherwise it's ready to ship
+'''
+
+import numpy as np
+import matplotlib.pyplot as plt
+from astropy.io import fits
+from pylanetary.utils import rebin
+from scipy.ndimage import gaussian_filter
+from scipy.signal import medfilt2d, convolve2d
+import paths
+from skimage.filters import difference_of_gaussians
+
+
+code = 'Mab'
+constants_dict = {
+    'Mab':{
[…]

### 2023-02-06 src/scripts/psf_wing_correction.py

@@ -15,6 +15,10 @@ Use standard star observations to compute the flux correction
 ready to ship!
 '''
 
+if not os.path.exists(paths.data / "tables"):
+    os.mkdir(paths.data / "tables")
+
+
 show_figures = False
 for filt in ['H', 'K']:
 
@@ -33,7 +37,7 @@ for filt in ['H', 'K']:
     for k, fname in enumerate(star_files):
         
         hdul = fits.open(fname)
-        print(fname)
+        #print(fname)
         data = hdul[0].data
         if filt == 'H':
             cutoff = 5800
@@ -41,7 +45,7 @@ for filt in ['H', 'K']:
             cutoff = 2500
         data[data>cutoff] = 0 #this removes bad pixels
         star_pos = np.unravel_index(np.argmax(data), data.shape)[::-1]
-        print(star_pos, np.max(data))
+        #print(star_pos, np.max(data))
         
         # flux from moon inner radius
         moon_aps = np.array([aperture.CircularAperture(star_pos, r=ri) for ri in ris])
@@ -52,7 +56,8 @@ for filt in ['H', 'K']:
         star_aps = [aperture.CircularAperture(star_pos, r=ro) for ro in ros]
         star_areas = [star_ap.area for star_ap in star_aps]
         star_apsums = [aperture.ApertureStats(data, star_ap).sum for star_ap in star_aps]
-        print('Total star counts = ', np.mean(star_apsums))
+        if __name__ == "__main__":
+            print('Total star counts = ', np.mean(star_apsums))
         
         # noise
         noise_anns = [aperture.CircularAnnulus(star_pos, r_in=ro, r_out=ro+noise_ann_width) for ro in ros]

### 2023-02-06 src/scripts/relative_position_miranda_puck.py

@@ -22,7 +22,7 @@ See if that triangle matches the true position of Mab
 Second test: flip the problem by overlaying the expected path of Miranda and Puck relative to 
     Mab on top of the detection image
 
-To do: make this generically accept any small moon or band
+ready to ship!
 '''
 
 code = 'Mab'
@@ -112,7 +112,7 @@ miranda_mab_vector =  np.array([x_shifts[0] - x_shifts[2], y_shifts[0] - y_shift
 
 expected_mab_position_1 = puck_position + puck_mab_vector
 expected_mab_position_2 = miranda_position + miranda_mab_vector
-print(expected_mab_position_1, expected_mab_position_2, mab_position)
+#print(expected_mab_position_1, expected_mab_position_2, mab_position)
 
 # plot the frame with these vectors on top
 fig, ax = plt.subplots(1,1, figsize = (8,8))
@@ -143,7 +143,7 @@ ax.set_ylabel('Pixels')
 ax.legend()
 
 fig.savefig(paths.figures / f"expected_position_{stem}_{code}_oneframe.png", dpi=300)
-plt.show()
+#plt.show()
 plt.close()
 
 ## do the flipped problem here: assume Mab position is correct and static on the detector
@@ -203,7 +203,7 @@ ax.set_ylabel('Pixels')
 ax.legend()
 
 fig.savefig(paths.figures / f"expected_position_{stem}_{code}.png", dpi=300)
-plt.show()
+#plt.show()
 plt.close()
 
 

### 2023-02-06 src/scripts/run_perturbation_experiment.py

@@ -1,10 +1,7 @@
 #!/usr/bin/env python
 
 '''
-runs shift_stack_moons on the 2019-10-28 Keck Uranus data
-
-TO DO:
-- get optimal detections of the other moons
+ready to ship
 '''
 
 from shift_stack_moons import shift_and_stack
@@ -44,8 +41,9 @@ tstart = date+' 00:00'
 tend = date+' 23:59'
 pixscale = 0.009971
 
-if not os.path.exists(paths.data / "results"):
-    os.mkdir(paths.data / "results")
+np.random.seed(9)
+if not os.path.exists(paths.data / "perturbation_experiment"):
+    os.mkdir(paths.data / "perturbation_experiment")
 
 
 for code in ['Mab']:
@@ -59,6 +57,7 @@ for code in ['Mab']:
     ephem = ephem.set_index(pd.DatetimeIndex(ephem["datetime_str"]))
     
     for band in ['H', 'Kp']:
+        print(f'Starting {band} band')
         stem = constants_dict[code][band]['stem']
         start_idx = constants_dict[code][band]['start_idx']
         end_idx = constants_dict[code][band]['end_idx']
@@ -85,10 +84,10 @@ for code in ['Mab']:
         # for testing, make a different frame the zeroth one
         if reverse:
             fnames = fnames[::-1]
-
-        # do shift-and-stack and write
-        fits_out = shift_and_stack(fnames, ephem, pixscale=pixscale, 
-                    difference=True, edge_detect=canny, perturbation_mode=False, diagnostic_plots = False)
-        fits_out.write(outfname)
-
-
+            
+        for i in range(100):
+            print(f"starting simulation {i} out of 100")
+            outfname2 = paths.data / f"perturbation_experiment/{stem}_{code}_{date}_{i}.fits"
+            fits_out = shift_and_stack(fnames, ephem, pixscale=pixscale, 
+                        difference=True, edge_detect=canny, perturbation_mode=True, diagnostic_plots = False)
+            fits_out.write(outfname2)

### 2023-02-09 src/scripts/compute_if.py
nearly done incorporating Imkes comments

@@ -23,8 +23,8 @@ caption = r'Available color information on Mab compared with its nearest orbital
 code = 'Mab'
 constants_dict = {
     'Mab':{
-        'H':{'stem':'urh', 'bp_file':paths.static / 'h.csv'}, 
-        'K':{'stem':'urk', 'bp_file':paths.static / 'kp.csv'}, 
+        'H':{'stem':'urh', 'bp_file':paths.static / 'h.csv', 'A':1}, # for integrated I/F use area of 1 km
+        'K':{'stem':'urk', 'bp_file':paths.static / 'kp.csv', 'A':1}, 
         },
     'Ophelia':{
         'H':{},
@@ -35,55 +35,59 @@ constants_dict = {
         'K':{},
         },
     'Perdita':{
-        'H':{},
-        'K':{},
+        'H':{'stem':'urh', 'bp_file':paths.static / 'h.csv', 'A':1}, 
+        'K':{'stem':'urk', 'bp_file':paths.static / 'kp.csv', 'A':1}, 
         },
 }
 
-# get sun-target and Earth-target distance from Horizons
-obscode = '568'
-date = '2019-10-28'
-tstart = date+' 11:00' #this just needs to be approximate
-tend = date+' 12:00'
-horizons_obj = Horizons(
-    id=code,
-    location=obscode,
-    epochs={"start": tstart, "stop": tend, "step": "1h"},
-)
-ephem = horizons_obj.ephemerides()[0]
-target_sun_dist = ephem['r']
-target_obs_dist = ephem['delta']
-target_omega = 1*u.km**2 / (((target_obs_dist*u.au).to(u.km))**2) #setting area to 1 km2 means that I/F function will output integrated I/F
-
-wls, fluxes, errs = [], [], []
-for band in ['H', 'K']:
-    # get Keck filter transmission
-    stem = constants_dict[code][band]['stem']
-    with open(paths.output / f'{code}_{stem}_flux.txt', 'r') as f:
-        flux = float(f.readline()) * 1e-16 # erg s-1 cm-2 um-1
-    with open(paths.output / f'{code}_{stem}_fluxerr.txt', 'r') as f:
-        flux_err = float(f.readline()) * 1e-16 # erg s-1 cm-2 um-1
-    bp_file = constants_dict[code][band]['bp_file']
-    wl, trans = np.genfromtxt(bp_file, skip_header=1, delimiter=',', usecols=(0,1)).T
-    wl = wl[~np.isnan(wl)][:-1] * u.micron
[…]

### 2023-02-09 src/scripts/path_on_detector.py

@@ -34,9 +34,15 @@ req = 25559 #km
 rpol = 24973 #km
 
 constants_dict = {
-    'H':{'stem':'urh', 'reverse':True, 'canny':False, 'start_idx':41, 'end_idx':64}, #urh156
-        'K':{'stem':'urk', 'reverse':True, 'canny':True, 'start_idx':0, 'end_idx':24}, #urk146
+    'Mab':{'H':{'stem':'urh', 'canny':False, 'start_idx':41, 'end_idx':64}, #urh156
+            'K':{'stem':'urk', 'canny':True, 'start_idx':0, 'end_idx':24}}, #urk146
+    'Perdita':{'H':{'stem':'urh', 'canny':False, 'start_idx':0, 'end_idx':48}, 
+            'K':{'stem':'urk', 'canny':True, 'start_idx':0, 'end_idx':11}}, 
+    'Cupid':{'H':{'stem':'urh', 'canny':False, 'start_idx':0, 'end_idx':64}, 
+            'K':{'stem':'urk', 'canny':True, 'start_idx':0, 'end_idx':24}}, 
         }
+# Cupid on detector in all K-band frames but should be reversed
+# Cupid on detector for frames 0-29, 48-64 in H-band and also should be reversed
 
 ## get ephemeris from Horizons. quantity 6 is the satellite relative position to parent in arcsec
 horizons_obj = Horizons(
@@ -50,9 +56,9 @@ ephem = ephem.set_index(pd.DatetimeIndex(ephem["datetime_str"]))
 exposure_starts = []
 filters = ['K', 'H']
 for filt in filters:
-    stem = constants_dict[filt]['stem']
-    start_idx = constants_dict[filt]['start_idx']
-    end_idx = constants_dict[filt]['end_idx']
+    stem = constants_dict[code][filt]['stem']
+    start_idx = constants_dict[code][filt]['start_idx']
+    end_idx = constants_dict[code][filt]['end_idx']
     fnames = [data_dir / s for s in data_files if s.startswith(stem)]
 
     # split into different observing blocks
@@ -106,7 +112,7 @@ for filt in filters:
 
     # print the average pixel motion per frame
     #print(vec_x[-1], vec_y[-1])
-    print(f'Average motion of Mab during a single exposure (pixels): {np.mean(vec_x)}, {np.mean(vec_y)}')
[…]

### 2023-02-09 src/scripts/photometry.py

@@ -21,6 +21,7 @@ import paths
 from scipy.interpolate import interp1d
 
 
+fluxcal_frac_err = 0.10 #check this number!
 photometry_constants_dict = {
     'Mab':{
         'H':{'stem':'urh', 'coadds':6, 'C1':8.87e-17, 'xpos':187, 'ypos':395}, #urh156
@@ -35,8 +36,8 @@ photometry_constants_dict = {
         'K':{},
         },
     'Perdita':{
-        'H':{},
-        'K':{},
+        'H':{'stem':'urh', 'coadds':6, 'C1':8.87e-17, 'xpos':262, 'ypos':306},
+        'K':{'stem':'urk', 'coadds':4, 'C1':6.46e-17, 'xpos':497, 'ypos':973},
         },
 }
 
@@ -50,12 +51,12 @@ def get_wing_corr(r, wing_corrs):
 
 ## compute the photometry for many inner and outer radii
 nsamples = 50
-ri0 = 5
+ri0 = 3
 ri1 = 10
 ro0 = ri1 + 5
 ro1 = 50
 
-for code in ['Mab']:
+for code in ['Mab', 'Perdita']:
     for band in ['H', 'K']:
         stem = photometry_constants_dict[code][band]['stem']
         n_coadds_raw = photometry_constants_dict[code][band]['coadds'] #apparently the "raw" images were already divided by the number of coadds so this is needed
@@ -144,10 +145,13 @@ for code in ['Mab']:
         print(f'Lower, upper error = {final_err} erg s-1 cm-1 um-1')
         print(f'Standard deviation = {final_std} erg s-1 cm-1 um-1')
         
+        # add the 20% flux cal uncertainty to the error
+        reported_uncertainty = np.sqrt(final_std**2 + (fluxcal_frac_err*final_flux)**2)
+        
         with open(paths.output / f"{code}_{stem}_flux.txt", "w") as f:
             print(f"{(1e16*final_flux):.1f}", file=f)
         with open(paths.output / f"{code}_{stem}_fluxerr.txt", "w") as f:
-            print(f"{(1e16*final_std):.1f}", file=f)
+            print(f"{(1e16*reported_uncertainty):.1f}", file=f)
                 
         fig, (ax0) = plt.subplots(1,1, figsize = (8,6))
         

### 2023-02-09 src/scripts/plot_perturbation_experiment.py

@@ -37,6 +37,7 @@ from scipy.ndimage import gaussian_filter
 from scipy.signal import medfilt2d, convolve2d
 import paths
 from skimage.filters import difference_of_gaussians
+from mpl_toolkits.axes_grid1.axes_divider import make_axes_locatable
 
 
 code = 'Mab'
@@ -106,12 +107,12 @@ for band in ['H', 'K']:
     ax0 = plt.subplot2grid((2,2),(0,1))
     ax1 = plt.subplot2grid((2,2),(1,1))
     
-    ax0.imshow(cs_rebin_real, origin='lower')
+    im0 = ax0.imshow(cs_rebin_real, origin='lower')
     ax0.set_title('Filtered and Binned Data')
-    ax2.imshow(cs_rebin, origin='lower')
+    im2 = ax2.imshow(cs_rebin, origin='lower')
     ax2.set_title('Example Test Frame, Filtered and Binned')
     
-    ax3.imshow(data_real, origin='lower', vmin=-30, vmax=50)
+    im3 = ax3.imshow(data_real, origin='lower', vmin=-30, vmax=50)
     ax3.set_title('Real Unfiltered Data')
     
     ax1.hist(detection_sizes, bins=10)
@@ -120,9 +121,15 @@ for band in ['H', 'K']:
     ax1.set_ylabel('Number of Test Frames')
     ax1.legend(loc = 'upper right')
     
-    for ax in [ax0, ax2, ax3]:
+    ims = [im0, im2, im3]
+    for j, ax in enumerate([ax0, ax2, ax3]):
         ax.set_xticks([])
         ax.set_yticks([])
+        
+        ax_divider = make_axes_locatable(ax)
+        cax = ax_divider.append_axes("bottom", size="9%", pad="2%")
+        cb = fig.colorbar(ims[j], orientation='horizontal', cax=cax, label='Flux (arb. units)')
+        
         
     panel_labels = ['(a)', '(b)', '(c)', '(d)']
     for i, ax in enumerate([ax3, ax0, ax2, ax1]):

### 2023-02-09 src/scripts/psf_wing_correction.py

@@ -25,15 +25,16 @@ for filt in ['H', 'K']:
     nsamples = 50
     ri0 = 3 #smallest moon aperture radius
     ri1 = 20 #largest moon aperture radius
-    ro0 = 100 #star aperture radius to capture all star flux; also sets inner radius of noise annulus
-    ro1 = 300
-    noise_ann_width = 100 #width of noise annulus starting at ro
+    ro0 = 150 #star aperture radius to capture all star flux; also sets inner radius of noise annulus
+    ro1 = 200
+    noise_ann_width = 50 #width of noise annulus starting at ro
     
     star_files = [paths.data / f"reduced/2019oct28" / s for s in os.listdir(paths.data / f"reduced/2019oct28/") if s.startswith(f'hd{filt}')]
     ris = np.linspace(ri0, ri1, nsamples)
     ros = np.linspace(ro0, ro1, nsamples)
     
-    
+    star_cts = []
+    star_errs = []
     for k, fname in enumerate(star_files):
         
         hdul = fits.open(fname)
@@ -56,8 +57,6 @@ for filt in ['H', 'K']:
         star_aps = [aperture.CircularAperture(star_pos, r=ro) for ro in ros]
         star_areas = [star_ap.area for star_ap in star_aps]
         star_apsums = [aperture.ApertureStats(data, star_ap).sum for star_ap in star_aps]
-        if __name__ == "__main__":
-            print('Total star counts = ', np.mean(star_apsums))
         
         # noise
         noise_anns = [aperture.CircularAnnulus(star_pos, r_in=ro, r_out=ro+noise_ann_width) for ro in ros]
@@ -75,6 +74,7 @@ for filt in ['H', 'K']:
         
         # compile all possible combinations of moon and star aperture sizes
         results_table = np.empty((len(moon_apsums), len(bkgds)))
+        star_fluxes = np.empty((len(bkgds)))
         for i in range(len(moon_apsums)):
             moon_apsum = moon_apsums[i]
             moon_area = moon_areas[i]
@@ -85,6 +85,8 @@ for filt in ['H', 'K']:
                 moon_flux = moon_apsum - (bkgd * moon_area)
                 
                 results_table[i,j] = moon_flux / star_flux
+                if i == 0:
+                    star_fluxes[j] = star_flux
                 
         fig, ax = plt.subplots(1,1, figsize = (8,8))
         cim = ax.contourf(ros, ris, results_table, levels=12)
@@ -97,11 +99,21 @@ for filt in ['H', 'K']:
             plt.show()
[…]

### 2023-02-09 src/scripts/shift_stack_uranus.py

@@ -8,6 +8,7 @@ TO DO:
 '''
 
 from shift_stack_moons import shift_and_stack
+#from shift_stack_moons.shift_stack_moons import *
 import numpy as np
 import matplotlib.pyplot as plt
 import os
@@ -25,13 +26,13 @@ constants_dict = {
         'H':{},
         'Kp':{},
         },
-    'Cordelia':{
-        'H':{},
-        'Kp':{},
+    'Cupid':{
+        'H':{'stem':'urh', 'reverse':True, 'canny':False, 'start_idx':9, 'end_idx':23, 'start_idx_2':48, 'end_idx_2':64},
+        'Kp':{'stem':'urk', 'reverse':True, 'canny':True, 'start_idx':0, 'end_idx':24},
         },
     'Perdita':{
-        'H':{},
-        'Kp':{},
+        'H':{'stem':'urh', 'reverse':False, 'canny':False, 'start_idx':0, 'end_idx':48},
+        'Kp':{'stem':'urk', 'reverse':False, 'canny':True, 'start_idx':0, 'end_idx':11},
         },
 }
 
@@ -48,7 +49,7 @@ if not os.path.exists(paths.data / "results"):
     os.mkdir(paths.data / "results")
 
 
-for code in ['Mab']:
+for code in ['Mab', 'Perdita']:
     ## get ephemeris from Horizons. quantity 6 is the satellite relative position to parent in arcsec
     horizons_obj = Horizons(
         id=code,
@@ -59,6 +60,7 @@ for code in ['Mab']:
     ephem = ephem.set_index(pd.DatetimeIndex(ephem["datetime_str"]))
     
     for band in ['H', 'Kp']:
+        print(f"Starting {code} {band}-band")
         stem = constants_dict[code][band]['stem']
         start_idx = constants_dict[code][band]['start_idx']
         end_idx = constants_dict[code][band]['end_idx']
@@ -80,7 +82,13 @@ for code in ['Mab']:
         fnames_sorted = np.array(fnames)[sorti]
         
         #select which observations you want - can separate them into blocks using block_starts and block_ends
-        fnames = fnames_sorted[start_idx:end_idx] #block_ends[-1]] #Mab is found in block_starts[5]+1 to end of block 7 for H-band
+        fnames = fnames_sorted[start_idx:end_idx]
+        if (code == 'Cupid') and (band == 'H'):
+            # customize because Cupid goes off the detector and back on
+            start_idx_2 = constants_dict[code][band]['start_idx_2']
[…]

### 2023-07-22 src/tex/ms.tex
publication accepted

@@
 % Title
-\title{Keck Near-Infrared Observations of Mab}
+\title{Keck Near-Infrared Detections of Mab and Perdita}
 
@@
 
-\author{Imke de Pater}
+\author[0000-0002-4278-3168]{Imke de Pater}
 \affiliation{Earth and Planetary Science Department, University of California, Berkeley, CA 94720, USA}
 
-\author{Chris Moeckel}
+\author[0000-0002-6293-1797]{Chris Moeckel}
 \affiliation{Earth and Planetary Science Department, University of California, Berkeley, CA 94720, USA}
 
+\linenumbers
+
 \begin{abstract}
-We report the first near-infrared detection of Uranus's smallest known moon Mab, the presumed source of the blue and diffuse $\mu$ ring, using the NIRC2 instrument at Keck Observatory.
-The detection was permitted by an updated shift-and-stack procedure allowing us to track Mab across the detector in 23 separate exposures taken over $\sim$2 hours, as well as the very low (0.02$^\circ$) phase angle at the time of observation.
+We report the first near-infrared detection of Uranus's \textbf{tiny} moon Mab, the presumed source of the blue and diffuse $\mu$ ring, using the NIRC2 instrument at Keck Observatory.
+The detection was permitted by an updated shift-and-stack procedure allowing us \textbf{to integrate on Mab as it moved} across the detector in 23 separate exposures taken over $\sim$2 hours, as well as the very low (0.02$^\circ$) phase angle at the time of observation.
 At this phase angle, Mab has an integrated I/F of 
@@
 at 1.6 $\mu$m and 
-\variable{output/Mab_urk_intif.txt} $\pm$ \variable{output/Mab_urk_intiferr.txt} km$^{2}$ 
+$\lesssim$\variable{output/Mab_urk_intif.txt} km$^{2}$ 
 at 2.1 $\mu$m. 
 Comparing these values with Mab's visible reflectance as derived by HST reveals that Mab is spectrally blue; its (0.5 $\mu$m)/(1.6 $\mu$m) color is more consistent with Miranda's value than Puck's value.
-We therefore propose that Mab is more likely a $\sim$6-km radius body with a Miranda-like surface than a 12-km radius body with a Puck-like surface, but we caution that a Puck-like color is only ruled out at the 2$\sigma$ level.
-We also report (the first?) infrared photometry of Ophelia, (Cordelia?), and Perdita.
+Mab is therefore more likely a $\sim$6-km radius body with a Miranda-like surface than a 12-km radius body with a Puck-like surface, in agreement with prior work based on infrared upper limits, but we caution that a Puck-like color is only ruled out at the 2$\sigma$ level.
+We also report the first infrared photometry of Perdita, finding an integrated I/F of 
+\variable{output/Perdita_urh_intif.txt} $\pm$ \variable{output/Perdita_urh_intiferr.txt} km$^{2}$ at 1.6 $\mu$m.
 \end{abstract}
 
-\keywords{}
+\keywords{Satellites, composition; Satellites, surfaces; Satellites, general; Uranus, satellites; Satellites, formation}
 
@@
 The small regular moons comprising the Portia group in the Uranian system represent the most densely-packed set of satellites known, with semimajor axis separations of 3\% on average \citep{showalter20}; as such, the system is predicted to be chaotic, with collisions occurring on 10$^5$- to 10$^7$-year timescales \citep{duncan97, french12}.
-Indeed, the faint dusty $\nu$ ring, situated between the orbits of Portia and Rosalind, has been proposed to be the remnant of such a collision.
-Due in part to this small orbital spacing, the Uranian satellites affect each other's geology via dust transport in the circumplanetary environment.
+Indeed, the faint dusty $\nu$ ring, situated between the orbits of Portia and Rosalind, has been proposed to be the remnant of such a collision \citep{showalter20}.
+Due in part to this small orbital spacing, the Uranian satellites likely affect each other's surface properties via dust transport in the circumplanetary environment.
 For example, dust deposition from Uranus's outer irregular satellites has been invoked to explain spectral reddening of the leading hemispheres of Ariel, Umbriel, Titania, and Oberon \citep{cartwright18}.
@@
 The faint, diffuse $\mu$ ring is therefore crucial for understanding the evolution of Uranus's circumplanetary system as a whole, but its properties and origin remain poorly understood.
-It is the only ring in the solar system with a blue spectrum other than Saturn's E ring, which is sourced from Enceladus's cryovolcanism \citep{depater06}.
+It is the only ring in the solar system with a blue spectrum other than Saturn's E ring \citep{depater06}, which is sourced from Enceladus's cryovolcanism \textbf{\citep{pang84, porco06, spencer06, spahn06}}.
 The E~ring is blue due to its abundance of tiny ($\lesssim$1 $\mu$m) particles and paucity of larger grains \citep{showalter91, depater04, hillier07}.
 The tiny moon Mab is embedded in, and is the presumed source of, the $\mu$ ring, but active cryovolcanism on such a small body seems highly unlikely.
-Instead, it has been proposed that Mab outbursts like the active Centaur Echeclus, with the blue color of the $\mu$ ring attributable not to small particle sizes but to a high abundance of carbon-rich organic matter \citep{seccull19}.
-Alternatively, interplanetary dust and/or charged plasma impacting Mab's surface may liberate enough particles to form the $\mu$ ring.
-To explain the blue color, the latter scenario relies on theoretical and numerical simulation expectations that $\sim$1 $\mu$m particles are more likely than larger particles to disperse into a ring (instead of re-accreting to the planet) under the combined influences of gravity, radiation pressure, and electromagnetic forces \citep{horanyi92, sfair09, sfair12}.
+Instead, interplanetary dust and/or charged plasma impacting Mab's surface may liberate enough particles to form the $\mu$ ring, as suggested by \citet{depater06} based on a model that was originally proposed to explain the blue color of the E~ring before Enceladus's geysers were discovered \citep{horanyi92, hamilton94}.
+This scenario relies on theoretical expectations that $\sim$1 $\mu$m particles are more likely than larger particles to disperse into a ring (instead of re-accreting to the moon) under the combined influences of gravity, radiation pressure, and electromagnetic forces.
+Numerical simulations of $\mu$ ring particles sourced by meteoritic collisions with Mab's surface found that $\sim$1 $\mu$m particles are more susceptible than larger particles to eccentricity perturbations and therefore spread out into a diffuse ring, whereas the larger particles remain confined near Mab's orbital radius \citep{sfair12}.
+That simulation thus predicted a radial color gradient in the ring; however, the model was unable to achieve a steady state, which the authors attribute to limited knowledge of how the particles are removed from the ring, so this expectation should be treated with caution.
+%Alternatively, it has been proposed that Mab outbursts like the active Centaur Echeclus \textbf{(M.
+Hedman, private correspondence??)}, with the blue color of the $\mu$ ring attributable not to small particle sizes but to a high abundance of carbon-rich organic matter \citep{seccull19}.
 In any case, the physical properties of this unusual moon are of interest for studies of interactions between airless surfaces and the interplanetary environment, the origin and dynamical evolution of circumplanetary dust, and the formation and evolution of small solar system bodies.
@@
 The HST observations that discovered Mab could not uniquely constrain its radius and albedo, which are degenerate with respect to the reflected flux of an unresolved body \citep{showalter06}.
-Those authors proposed two end-member cases: Mab has a $\sim$6 km radius with a Miranda-like icy surface and an albedo of $\sim$0.46; or Mab has a $\sim$12 km radius and an albedo of $\sim$0.1, indicating the presence of dark organic compounds on its surface like its other nearest neighbor, Puck.
-A previous near-infrared search with Keck did not detect the moon, leading to the proposal that Mab's radius is $\lesssim$6 km and as dark at wavelengths from 1.6-2.4 $\mu$m as Puck \citep[albedo $\lesssim$0.11;][]{paradis19, paradis23}.
-Strong near-IR absorption from water ice could partially account for this darkening; however, the decrease in brightness is not expected to exceed 50\% even for a very icy body \citep[c.f.
-Haumea, one of the purest amorphous ice surfaces in the solar system;][]{gourgeot16}.
+Those authors proposed two end-member cases: Mab has a $\sim$6 km radius with a Miranda-like icy surface and an albedo of $\sim$0.46, or Mab has a $\sim$12 km radius and an albedo of $\sim$0.1 like its other nearest neighbor, Puck.
+Previous near-infrared searches with Keck did not detect the moon; \textbf{the upper limit of \citet{depater06} led to the suggestion that Mab was an icy body like Miranda, with substantial water-ice absorption, and the more sensitive upper limit of \citet{paradis19} required that Mab's radius be $\lesssim$6 km and its surface} as dark at 1.6 $\mu$m as Puck \citep[albedo $\lesssim$0.11;][]{paradis23}.
+Strong near-IR absorption from the crystalline water ice band at 1.65 $\mu$m is responsible for a factor-of-four darkening in the near-IR spectra of Pluto's outer satellites Nix and Hydra \citep{cook18}, and this absorption band could explain such a low H-band flux.
+Note that the decrease in brightness between visible and 1.6 $\mu$m wavelengths from amorphous water ice absorption \textbf{cannot account for this factor of four \citep[][]{mastrapa08, terai16}, which would imply that Mab's surface is overlain with crystalline rather than amorphous water ice}.
 
-Here we present the first observations of Mab at near-infrared wavelengths.
-Our dataset and data proceessing steps are described in Section \ref{s:observations}.
-We present photometry of Mab, as well as Cordelia, Ophelia, and Perdita, in Section \ref{s:results}, and compare Mab's derived infrared reflectance with the spectra of Miranda and Puck in Section \ref{s:discussion}.
+Here we present the first detection of Mab at near-infrared wavelengths.
+We also report the first near-IR detection of \textbf{the tiny Portia group satellite Perdita, which to date has been observed only in a reanalysis of Voyager 2 data \citep{karkoschka01b} and the same HST dataset that first detected Mab \citep{showalter06}.} Our dataset and data proceessing steps are described in Section \ref{s:observations}.
+We present photometry of Mab and Perdita in Section \ref{s:results}, and compare the derived infrared reflectance of those two moons with the spectra of Miranda and Puck in Section \ref{s:discussion}.
 
@@
 
-This paper makes use of H- and Kp-band data taken on 28 October 2019 by the narrow camera of the NIRC2 instrument coupled to the Adaptive Optics (AO) system at Keck Observatory, using Uranus itself for wavefront sensing \citep{wizinowich00, vandam04}.
+This paper makes use of H\textbf{-band (1.6 $\mu$m)} and Kp-band \textbf{(2.1 $\mu$m)} data taken on 28 October 2019 by the narrow camera of the NIRC2 instrument coupled to the Adaptive Optics (AO) system at Keck Observatory, using Uranus itself for wavefront sensing \citep{wizinowich00, vandam04}.
 The same data were analyzed by \citet{paradis23}, so we refer the reader to that paper for a detailed description of the observation and data reduction procedures.
-The standard star was FS2 from the UKIRT Faint Standard Star list,\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc/UKIRTstds.html}} and standard photometric calibration procedures resulted in calibration constants $C_H = 8.87\times10^{-17}$ and $C_K = 9.11\times10^{-17}$ to convert from 1 count per second to 1 \ergsec{}.
-The uncertainty in the photometric calibration was estimated from the spread in measured fluxes from the standard star between frames.
-The value we found was 20\% in both filters, which is typical for NIRC2 observations \citep{depater14, molter19}.
+The standard star was FS2 from the UKIRT Faint Standard Star list \citep{hawarden01},\footnote{\url{https://www2.keck.hawaii.edu/inst/nirc/UKIRTstds.html}} and standard photometric calibration procedures resulted in calibration constants $C_H = 8.87\times10^{-17}$ and $C_{Kp} = 6.46\times10^{-17}$ to convert from 1 count per second to 1 \ergsec{}.
+We derived the photometric uncertainty by looking at the frame-by-frame surface brightness variations of cloud-free regions of Uranus's disk, which are very stable over the timescales considered here.
+We determined the surface brightness of the planet in two 20 $\times$ 20 pixel regions of the disk in both H- and Kp-band, one just north of Uranus's equator and one just south of the North Pole.
+The night was very photometrically stable, and the frame-by-frame variance displayed no clear temporal trends in either H- or Kp-band in either region; the fluctuations looked like Gaussian noise with standard deviations of
+\variable{output/urh_photometric_uncertainty_percent.txt}\% in H-band and \variable{output/urk_photometric_uncertainty_percent.txt}\% in Kp-band.
+These numbers agree with the spread in the fluxes derived from the three standard star frames, and we take them to be the 1$\sigma$ photometric calibration uncertainty.
+The uncertainty in the true flux of the standard star FS2 is less than one part per thousand \citep{hawarden01}.
 
-Our full dataset consisted of 23 exposures of 120 seconds each in H-band (1.6 $\mu$m) and 24 exposures of 120 seconds each in Kp-band (2.1 $\mu$m); these were all the frames taken on 28 October 2019 in which Mab's expected position was inside the field of view of the narrow camera (Figure \ref{fig:detection}, left panel).
+Our full dataset consisted of 23 exposures of 120 seconds each in H-band and 24 exposures of 120 seconds each in Kp-band; these were all the frames taken on 28 October 2019 in which Mab's expected position was inside the field of view of the narrow camera (Figure \ref{fig:detection}, left panel).
 The proper motion of Mab is roughly 30 mas (3 pixels) per minute, which means that each frame had to be shifted relative to the previous one in accordance with Mab's expected vector of motion to improve the signal-to-noise ratio (SNR).
 This so-called ``shift-and-stack" technique has been used by other authors to improve the SNR of moving point sources, including to measure photometry of other small moons of Uranus with NIRC2 \citep[][]{paradis19, paradis23}.
-Our shift-and-stack procedure differs in several ways from the one implemented by those authors, and we describe it fully in Appendix \ref{s:shiftandstack}.
-The application of shift-and-stack resulted in one stacked image per filter at the expected position of Mab, representing effective integration times of 2760 seconds in H-band and 2880 seconds in Kp-band.
+Our shift-and-stack procedure differs in several ways from the one implemented by those authors, and we describe it fully in Supplementary Material \ref{s:shiftandstack}.
+The application of shift-and-stack resulted in one stacked image per filter at the expected position of Mab, representing effective integration times of 46 minutes in H-band and 48 minutes in Kp-band.
 
 \begin{figure}
-\includegraphics[width=0.5\textwidth]{figures/motion_on_detector.png}
+\includegraphics[width=0.5\textwidth]{figures/motion_on_detector_Mab.png}
 \includegraphics[width=0.5\textwidth]{figures/detection_images_Mab.png}
-\caption{\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected position of Mab in each of our 23 H-band and 24 Kp-band exposures.
+\caption{\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected position of Mab in each of our 23 H-band (blue) and 24 Kp-band (red) exposures.
 The bright and faint point sources visible in the image are Miranda and Puck, respectively.
-\textbf{Right:} Detection of Mab in H-band (top panel) and tentative detection in Kp-band (bottom panel) using the shift-and-stack technique.\label{fig:detection}}
+\textbf{Right:} Detection of Mab in H-band (top panel) and non-detection in Kp-band (bottom panel) using the shift-and-stack technique.\label{fig:detection}}
 \end{figure}
@@
 
-\subsection{Photometry of Mab}
-
 An image of our H-band detection of Mab is shown in the upper right panel of Figure \ref{fig:detection}.
-The detection is in a low-SNR regime, but we are confident that it is real for three reasons.
-First, a tentative detection of Mab can be made separately from the first 11 frames and the last 11 frames, meaning that an artefact in a single frame or 8-frame group is not producing a false positive.
+The detection \textbf{has a low SNR}, but we are confident that it is real for three reasons.
+First, a tentative detection of Mab can be made separately from the first 11 frames and the last 11 frames, meaning that an artifact in a single frame or 8-frame group is not producing a false positive.
 Second, the detection is located in the appropriate position on the sky relative to Miranda and Puck, as discussed below.
@@
 In short, we added random offsets to the expected position of Mab in each frame, then carried out shift-and-stack in the same way as we did for the true expected position.
-We repeated this procedure with different random offsets 100 times, and found that no noise spikes as bright as our Mab detection appeared anywhere in any of those 100 stacks; see Appendix \ref{s:falsepositives} for more details.
+We repeated this procedure with different random offsets 100 times, and found that no noise spikes as bright as our Mab detection appeared anywhere in any of those 100 stacks; see Supplementary Material \ref{s:falsepositives} for more details.
 
-Because Mab was detected at low SNR and within a substantial scattered light background, the flux in the wings of the PSF could not be accurately measured.
-We therefore determined the flux of Mab using a flux bootstrapping procedure similar to that applied to Keck-observed point sources by many other authors \citep[e.g.,][]{gibbard05, molter19, paradis23}, the specifics of which we summarize in Appendix \ref{s:bootstrapping}.
+Because Mab was detected at low SNR and within a substantial scattered light background, the flux in the wings of the point-spread function (PSF) could not be measured.
+We therefore determined the flux of Mab using a flux bootstrapping procedure similar to that applied to Keck-observed point sources by other authors \citep[][]{gibbard05, depater14b, molter19, paradis23}, the specifics of which we summarize in Supplementary Material \ref{s:bootstrapping}.
 We find the total flux of Mab to be
 (\variable{output/Mab_urh_flux.txt} $\pm$ \variable{output/Mab_urh_fluxerr.txt})$\times10^{-16}$ \ergsec{} 
-in H-band, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the flux bootstrapping error and the 20\% photometric calibration error.
-This flux level corresponds to an integrated I/F of
+in H-band, where the error bars indicate a 1-$\sigma$ uncertainty, computed by taking the quadrature sum of the $\sim$13\% flux bootstrapping error and the $\sim$2\% photometric calibration error.
+
+\textbf{It is typical to express visible and infrared fluxes of solar system bodies in terms of the unitless quantity I/F, which is defined as
+\begin{equation}
+\frac{I}{F} = \frac{R^2}{\Omega} \frac{F}{F_\odot}
+\end{equation}
+where $R$ is the heliocentric distance to the body in AU, $\Omega$ is the solid angle of the body $F$ is the observed flux of the body, and $\pi F_\odot$ is the incident flux of the Sun at the distance to Earth in the same filter and the same units as $F$ \citep{hammel89}.
+In the case that the shape of the body, and therefore $\Omega$, is unknown, the integrated I/F is used instead, which is} defined as the sky-projected area the moon would have if it were a perfect Lambertian reflector \citep[i.e., \textbf{an I/F} of unity;][]{karkoschka01}.
+The flux level we observe for Mab corresponds to an integrated I/F of
 \variable{output/Mab_urh_intif.txt} $\pm$ \variable{output/Mab_urh_intiferr.txt} km$^{2}$ 
-at 1.6 $\mu$m, where the integrated I/F is defined as the sky-projected area the moon would have if it were a perfect Lambertian reflector \citep[i.e., a geometric albedo of unity;][]{karkoschka01}.
-Note that the Sun-target-observer phase angle $\alpha$ of these observations was only 0.02$^\circ$, so the opposition surge was likely substantial, as discussed more in Section \ref{s:discussion}.
-The sub-solar longitude of Mab passed through 270$^\circ$ during the $\sim$2 hours of observations and the sub-observer latitude was 46$^\circ$, so the reflectance values we report represent an average of the leading and trailing hemispheres.
+at 1.6 $\mu$m.
+Note that the Sun-target-observer phase angle $\alpha$ of these observations was only 0.02$^\circ$, so the opposition surge was likely substantial.
+The sub-observer longitude of Mab passed through 270$^\circ$ during the $\sim$2 hours of observations.
+\textbf{Therefore, assuming Mab is tidally locked, we observed mostly its trailing hemisphere and north pole.}
 
-The observed position of Mab is the same as expected based on the orbital parameters in the JPL Horizons system\footnote{\url{https://ssd.jpl.nasa.gov/horizons/app.html\#/}} to within one Keck resolution element; see Figure \ref{fig:astrometry}.
-We determined this based on the relative positions of Mab, Miranda, and Puck, the latter two of which can be seen easily in a single 120-second frame.
-The advantage of using the positions of other moons as a reference for astrometry is that it does not depend on a navigation solution for the planet's disk.
+The observed position of Mab is the same as expected based on the orbital parameters in the JPL Horizons system\footnote{\url{https://ssd.jpl.nasa.gov/horizons/app.html\#/}} to within one Keck resolution element ($\pm$20 mas or $\pm$270 km).
+We determined this based on the relative positions of Mab, Miranda, and Puck, the latter two of which can be seen easily in a single 120-second frame; see Figure \ref{fig:astrometry}.
+The advantage of using the positions of other moons as a reference for astrometry is that it does not depend on a navigation solution for the planet's disk nor the accuracy of the telescope pointing.
+\textbf{Previously-reported large residuals in Mab's orbit solution \citep{showalter06} were caused by a 0.13\% plate scale error in the HST HRC/Clear filter \citep{showalter19}, and this has already been corrected in the JPL Horizons system.
+Our detection confirms the accuracy of that solution to within the above-stated uncertainty.}
 
@@
 \caption{Two visualizations of Mab's expected position.
-\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected relative positions of Mab, Miranda, and Puck (red arrows) as well as the detected position of Mab (blue dot).
+\textbf{Left:} A single NIRC2 H-band exposure overlaid with the expected relative positions of Mab, Miranda, and Puck (red arrows) as well as the detected position of Mab (purple circle).
 The expected vector of motion of Mab is also overlain (blue arrow).
@@
 This feature is not clearly distinguishable by eye from positive noise spikes elsewhere in the frame.
-The false positive rate experiment discussed in Appendix \ref{s:falsepositives} shows that a noise spike of similar brightness would appear within $\sim$50 pixels of the expected position $\sim$\variable{output/perturbation_percent_higher_K.txt}\% of the time.
-However, our uncertainty in Mab's position is roughly one H-band PSF FWHM, or $\pm 2$ pixels, because we detected Mab at the expected position in H-band.
-We therefore label this a tentative detection.
-Photometry was performed in an identical way as for the H-band data, and we found a flux of
-(\variable{output/Mab_urk_flux.txt} $\pm$ \variable{output/Mab_urk_fluxerr.txt})$\times10^{-16}$ \ergsec{} 
-. This corresponds to an integrated I/F of 
-\variable{output/Mab_urk_intif.txt} $\pm$ \variable{output/Mab_urk_intiferr.txt} km$^{2}$ 
-at 2.1 $\mu$m, again at phase angle 0.02$^\circ$.
+The false positive rate experiment discussed in Supplementary Material \ref{s:falsepositives} shows that a noise spike of similar brightness would appear within $\sim$50 pixels of the expected position $\sim$\variable{output/perturbation_percent_higher_K.txt}\% of the time.
+We therefore consider this a non-detection.
+Based on that experiment, we can see that a point source whose PSF had a maximum brightness value of 5 times the per-pixel RMS noise would have been clearly detectable.
+By this definition, the \textbf{5-$\sigma$} upper limit to Mab's Kp-band flux is
+$\lesssim$\variable{output/Mab_urk_flux.txt}$\times10^{-16}$ \ergsec{}. 
+This corresponds to an integrated I/F of 
+$\lesssim$\variable{output/Mab_urk_intif.txt} km$^{2}$ 
+at 2.1 $\mu$m, \textbf{in line with the previous K-band 3$\sigma$ upper limit of $\lesssim$30 km$^2$ derived from single 120-second exposures \citep{depater06}.}
 
-\subsection{Photometry of Other Moons}
-
-We report the detection of Ophelia in H- and Kp-band and Perdita in H-band [CHECK K-BAND AGAIN].
-Something about Cordelia! do we actually see it?
-tie in story about median subtraction of frames.
-Try Cupid again.
+We also report \textbf{the first infrared} detection of Perdita in H-band with a flux of
+(\variable{output/Perdita_urh_flux.txt} $\pm$ \variable{output/Perdita_urh_fluxerr.txt})$\times10^{-16}$ \ergsec{}.
+This translates to an integrated I/F of \variable{output/Perdita_urh_intif.txt} $\pm$ \variable{output/Perdita_urh_intiferr.txt} km$^2$ at $\alpha=0.02^\circ$.
+We derive a Kp-band upper limit of $\lesssim$\variable{output/Perdita_urk_flux.txt}$\times10^{-16}$ \ergsec{}.
+\textbf{The sub-observer longitude was near 200$^\circ$ at the time of observation, i.e., near the anti-Uranus point.}
+\textbf{Like Mab, Perdita was detected at its expected orbital longitude to within one Keck H-band resolution element, or ($\pm$20 mas or $\pm$270 km).}
 
@@
 
-The infrared brightness of Mab was approximately a factor of two fainter than that observed by \citet{showalter06} with HST at 0.5 $\mu$m.
-We compare the I/F of Mab in the three available filters (HST clear, H, Kp) with I/F values in the same filters for Puck and Miranda \citep{karkoschka01, gibbard05, paradis23} in Figure \ref{fig:spectrum} assuming Mab has either a 6-km or 12-km radius.
-Ratios between these filters are compiled in Table \ref{tab:color}.
-The visible/H ratio of Mab, which has the lowest uncertainty, is within 1$\sigma$ of Miranda's visible/H ratio but $\sim$2$\sigma$ away from Puck's.
-We therefore marginally prefer the interpretation that Mab is a 6-km body with a Miranda-like water-ice-rich surface; however, the alternative interpretation that Mab is a 12-km body with a Puck-like surface rich in organic aerosols cannot be ruled out by the available data.
+The infrared brightness of Mab is approximately a factor of 2 fainter than observed by \citet{showalter06} with HST in the \textbf{HRC/Clear filter centered at} 0.5 $\mu$m.\textbf{\footnote{A factor of 1.6 discrepancy between the photometric calibration of HST's HRC/clear filter and the other filters was seen by \citet{showalter06}; those authors multiplied all of their results by this factor of 1.6, and we are using the published final (i.e., corrected) values here.}} We compare the I/F of Mab in the three available filters (HST HRC/clear, H, Kp) with I/F values in the same filters for Puck and Miranda \citep{karkoschka01, gibbard05, paradis23} in Figure \ref{fig:spectrum} assuming Mab has either a 6-km or 12-km radius.
+Ratios between these filters are compiled in Table \ref{tab:color}; \textbf{large ratios likely indicate an icy surface, as explained in the Introduction.}
+The visible/H ratio of Mab is 
+%\variable{whatever} $\pm$ \variable{whatever},
+closer to Miranda's visible/H ratio than that of Puck.
+We therefore prefer the interpretation that Mab is a 6-km body with a Miranda-like water-ice-rich surface; however, the alternative interpretation that Mab is a 12-km body with a Puck-like surface cannot be definitively ruled out by the available data.
 
 \variable{output/color_table.tex}
+
+\citet{karkoschka01b} determined a radius of 15 $\pm$ 3 km for Perdita assuming its reflectivity at $\alpha=16^\circ$ was 0.033, the average value for the Portia group.
+For a more direct comparison to our H-band observations, we rescaled Perdita's visible reflectivity from $\alpha = 16^\circ$ to $\alpha = 0.02^\circ$ according to the average Portia group phase curve given by \citet{karkoschka01}.
+This yields an integrated I/F of $54 \pm 22$ km$^2$ at visible wavelengths, and this is the value we used to derive the color information in Table \ref{tab:color}.
+\textbf{The large uncertainty on Perdita's visible/infrared color precludes any definitive statements about that moon's composition.}
 
@@
 Keck H- and Kp-band data for Puck are from \citet{paradis23} ($\alpha$ = 0.02$^\circ$).
-HST Mab data are from \citet{showalter06} ($\alpha$ = 0.08$^\circ$.)}
+HST Mab data are from \citet{showalter06} ($\alpha$ = 0.08$^\circ$).}
 \label{fig:spectrum}
@@
 (\variable{output/Mab_urh_flux.txt} $\pm$ \variable{output/Mab_urh_fluxerr.txt})$\times10^{-16}$ \ergsec{} 
-is seemingly in tension with the 3$\sigma$ upper limit of $2.4 \times 10^{-16}$ \ergsec{} derived previously \citep[][]{paradis19}, which we have rescaled to account for updated photometric calibration constants reported in \citet{paradis23}.
-However, those observations were taken at a phase angle of $0.65^\circ$.
-If we rescale the limit to the $0.02^\circ$ phase angle of our observations according to the \citet{karkoschka01} photometric model for Miranda, the limit would be $3.2 \times 10^{-16}$ \ergsec{}, within 2$\sigma$ of our derived result and therefore statistically insignificant.
-The \citet{paradis23} requirement that Mab's H-band geometric albedo be $<0.11$ for a 6-km effective radius is disfavored by our data at the 2.0$\sigma$ level.
+for Mab is seemingly in conflict with the 3$\sigma$ upper limit of $2.4 \times 10^{-16}$ \ergsec{} derived previously \citep[][]{paradis19}, which we have rescaled to account for updated photometric calibration constants reported in \citet{paradis23}.
+However, those observations were taken at a phase angle of $2.02^\circ$.
+If we rescale the limit to the $0.02^\circ$ phase angle of our observations according to the \citet{karkoschka01} photometric model for Miranda, the limit would be $3.9 \times 10^{-16}$ \ergsec{}, which is 2.8$\sigma$ from our value.
+\textbf{One possible explanation for this factor-of-1.6 discrepancy is that Mab has an oblong shape, and the orbital longitude of our observations was more conducive to observing a larger cross-sectional area than that of \citet{paradis19}.
+The similarly-sized Saturnian moons Calypso and Atlas, for example, have triaxial ellipsoid radii $a:b:c$ of approximately 5:3:2 and 2:2:1 \citep{thomas20}, so it is reasonable to expect factor-of-two differences in cross-sectional area.
+However, more detailed studies of the light curve of Mab over its orbit would be required to achieve trustworthy constraints on the moon's shape.}
+
+\textbf{
+Although the present results are suggestive of compositional differences among Uranus's small moons, the large uncertainty on the radii of both Mab and Perdita limit the physical interpretation available from photometry alone.
+Studies in the near future with the James Webb Space Telescope (JWST) will remedy this: JWST's mid-infrared instrument is sensitive enough to likely detect thermal emission from both moons \citep{wright23}, permitting size determinations via thermal radiometry, as has been routinely performed on asteroids and Kuiper Belt Objects \citep[see][for definition and examples of this technique]{muller02, stansberry08, vilenius18}.
+}
+
+%The \citet{paradis23} requirement that Mab's H-band geometric albedo be less than 0.11 for a 6-km effective radius is disfavored by our data at the 3.5$\sigma$ level.
 
@@
 
+This research was supported by NASA grant NNX16AK14G through
+the Solar System Observations (SSO) program to the University of
+California, Berkeley.
+
 The data presented herein were obtained at the W.
@@
 We are most fortunate to have the opportunity to conduct observations from this mountain.
+
+We thank the two referees, Luke Dones and one anonymous person, for their insightful comments and suggestions, which substantially improved the manuscript.
 
@@
 \url{https://github.com/emolter/mab}, and the release
-v.X.X allows anyone to re-build the entire manuscript. The datasets
-are stored at \url{https://doi.org/whatever}.
+v0.0.2 allows anyone to re-build the entire manuscript. The datasets
+are stored at \url{https://doi.org/10.5281/zenodo.7689583}.
 
@@
 scipy \citep{scipy20},
-shift\_stack\_moons \cite{shift_stack_moons23}
+shift\_stack\_moons \citep{shift_stack_moons23}
 }
-% other \software here!
 
-\facility{Keck:II}
+\facility{Keck:II (NIRC2)}
 
@@
 To improve the SNR on Mab, individual 120-second frames were shifted according to the expected position of the moon relative to Uranus and then co-added; details of this procedure are presented here.
-The accuracy of the shift-and-stack procedure depends sensitively on the rotation angle of the detector, so we corrected for the 0.26$^\circ$ angular offset between NIRC2's sky north position and true sky north before starting \citep{service16}.
+The accuracy of the shift-and-stack procedure depends on the rotation angle of the detector, so we corrected for the 0.26$^\circ$ angular offset between NIRC2's sky north position and true sky north \citep{service16}.
 First, we aligned the position of Uranus in all the frames using the \texttt{chi2\_shift} function of the \texttt{Astropy}-affiliated \texttt{image\_registration} Python package\footnote{\url{https://github.com/keflavich/image_registration}}, which implements the single-step discrete Fourier transform (DFT) algorithm for efficient sub-pixel image registration \citep{guizarsicairos08}.
 In Kp-band, cloud features and moons are brighter than the planet's disk, so we first applied a Canny edge-detection filter using the \texttt{skimage} Python package \citep{skimage14} to enhance the rings of Uranus, then ran \texttt{chi2\_shift} on those edges.
-This alignment method was found to produce very sharp stacked images of the rings, so we were confident that it was aligning the frames accurately.
+This alignment method was found to produce very sharp stacked images of the rings, so we were confident that it aligned the frames accurately.
 The implementation of this alignment step permitted us to co-add all three H-band observing blocks (and two Kp-band observing blocks) shown in Figure \ref{fig:detection}, between which Uranus was repositioned on the detector by tens of pixels.
@@
 Finally, we applied the shifts using a 2-D fast Fourier transform (FFT) sub-pixel image shift, again implemented with \texttt{image\_registration}, and summed all the frames to produce a single stacked frame.
-Our shift-and-stack code is publicly available on GitHub \citep{molter23}.
+Our shift-and-stack code is publicly available on GitHub \citep{shift_stack_moons23}.
 
@@
 Using the \texttt{astropy}-affiliated \texttt{photutils} package \citep{photutils140}, we measured the total flux inside many circular apertures of different radii $r_i$ centered on Mab; let us call Mab's flux for the $i$th radius $F_{M i}$.
-We then measured the flux inside apertures of the same size but centered on the standard star; call these $F_{\star i}$.
-Comparing $F_{\star i}$ with the true flux of the standard star $F_\star$ (as measured in a very large aperture of radius $\gtrsim$100 pixels) yielded a correction at a given value of $r_{i}$ given by simply $C_{psf} = F_{\star i}/F_\star$.
 The flux of the background must be subtracted in order to accurately determine $F_{M i}$; we defined the background region using a circular annulus centered on Mab with inner radius $r_i + 5$ pixels and outer radius $r_o$.
@@
 We also varied $r_o$ over a range of values to test the sensitivity of our flux estimate to the choice of background region.
-The flux of Mab $F_{i,o}$ for a given $r_i, r_o$ pair is given by $F_M = (F_{M i} - F_{B o}) / C_{psf}$.
-%, and the value of $F_{i,o}$ is displayed as a function of $r_i$ and $r_o$ in Figure \ref{fig:wing}. 
-The final flux estimate of Mab is given by the mean of $F_{i,o}$ over a reasonable range of $r_i$ and $r_o$ values, which we take to be 6-10 pixels and 15-50 pixels, respectively.
+We then measured the flux inside apertures of the same size but centered on the standard star; call these $F_{\star i}$.
+The same background regions were also applied to the standard star, yielding one star flux measurement $F_{\star i,o}$ for each inner and outer radius pair.
+Comparing $F_{\star i,o}$ with the true flux of the standard star $F_\star$ (as measured in a very large aperture of radius $\gtrsim$100 pixels) yielded a correction at given values of $r_i$ and $r_o$ given by simply $C_{psf,i,o} = F_{\star i,o}/F_\star$.
+The flux of Mab $F_{i,o}$ for a given $r_i, r_o$ pair is given by $F_M = (F_{M i} - F_{B o}) / C_{psf,i,o}$.
+The final flux estimate of Mab is given by the mean of $F_{i,o}$ over a reasonable range of $r_i$ and $r_o$ values, which we take to be 3-10 pixels and 15-50 pixels, respectively.
 The uncertainty is given by the standard deviation of $F_{i,o}$, which was $\approx$15\% in both H- and Kp-band.
-This error was multiplied in quadrature with the typical 20\% flux calibration error from standard star observations with Keck.
+This error was added in quadrature with the photometric uncertainty.
 
@@
 
-Mab was observed in the lower-left quadrant of the NIRC2 NARROW camera, which is known to have non-Gaussianity in its noise statistics,\footnote{https://www2.keck.hawaii.edu/inst/nirc2/ObserversManual.html} including vertical stripes of correlated noise.
+Mab was observed in the lower-left quadrant of the NIRC2 narrow camera, which is known to have non-Gaussianity in its noise statistics,\footnote{https://www2.keck.hawaii.edu/inst/nirc2/ObserversManual.html} including vertical stripes of correlated noise.
 Given the low SNR of the detection, it is natural to wonder whether the shift-and-stack technique is injecting false positives by stacking noise spikes atop one another.
-To test whether this is the case, we performed an experiment to test the false positive rate within the same detector noise and scattered light environment of the data, as follows.
-The expected position of Mab was shifted by a random x,y offset of mean amplitude 20 pixels in each frame, then the shift-and-stack algorithm was re-run assuming these new randomly-selected shifts and the output frame was saved.
+To determine whether this is the case, we performed an experiment to test the false positive rate within the same detector noise and scattered light environment of the data, as follows.
+The expected position of Mab was shifted by a random x,y offset of mean amplitude 20 pixels in each frame, then the shift-and-stack algorithm was re-run assuming these new randomly-selected shifts, and the output frame was saved.
 This experiment was repeated 100 times with different random offsets applied.
-We then searched for point sources in these 100 test stacks by applying a center-surround (difference-of-Gaussians) filter with an FWHM of 4 pixels for the inner Gaussian\footnote{This corresponds roughly to the diffraction-limited beam size of Keck in H-band.} and an FWHM of 12 pixels for the outer Gaussian.
+We then searched for point sources in these 100 test stacks by applying a center-surround (difference-of-Gaussians) filter with an FWHM of 4 pixels for the inner Gaussian (this corresponds roughly to the diffraction-limited beam size of Keck in H-band) and an FWHM of 12 pixels for the outer Gaussian.
 The center-surround filter is the appropriate choice because it accentuates features at the desired spatial frequency and downweights low spatial frequency features.
 The visual systems of humans and other animals employ center-surround antagonism \citep{graham06}, so this technique is a reasonable proxy for ``by-eye'' detection.
-We binned the filtered images by a factor of 2 in each direction.
-Finally, we computed the amplitude of the brightest pixel in each binned frame in units of the RMS noise of the input image.
-This yielded a rough estimate of the signal-to-noise ratio of that peak.
+We binned the filtered images by a factor of 2 in each direction so that a single pixel was more closely representative of a feature at the desired spatial frequency.
+Finally, we computed the amplitude of the brightest pixel in each binned frame.
 Identical filtering, binning, and SNR calculations were run on the real data.
-The detection of Mab in the real data was found to have a higher SNR than any peak in any of the 100 test frames in H-band (see Figure \ref{fig:randomstack}).
-In Kp-band, we find that a noise spike with an amplitude higher than our tentative detection is present in 8 out of 100 frames (Figure \ref{fig:randomstack_K}).
-However, because our tentative detection is in the correct position on the detector relative to Miranda and Puck, we feel justified in labeling it a tentative detection rather than a non-detection.
+The detection of Mab in the real data was found to be brighter than any peak in any of the 100 test frames in H-band (see Figure \ref{fig:randomstack}).
+In Kp-band, we find that a noise spike with an amplitude higher than our tentative detection is present in \variable{output/perturbation_percent_higher_K.txt} out of 100 frames (Figure \ref{fig:randomstack_K}), so we label it a non-detection.
 We tested other choices of inner and outer FWHM for the center-surround filter and different amounts of binning, and found that the results remained similar within reasonable ranges of these parameters.
-The SNR values reported in Figures \ref{fig:randomstack} and \ref{fig:randomstack_K} may look surprisingly high; note that they represent the detection level above the per-pixel RMS noise in the image, but these values do not correlate well with the true confidence level of a detection due to the substantial spatial correlation of the noise.
 

### 2023-07-22 src/scripts/compute_if.py

@@ -18,13 +18,13 @@ description of types of albedo: https://the-moon.us/wiki/Albedo
 To do: make work for the other moons, put them in the paper too
 '''
 
-caption = r'Available color information on Mab compared with its nearest orbital neighbors, Puck and Miranda. See Figure \ref{fig:spectrum} caption for data sources. \label{tab:color}'
+caption = r'Available color information on Mab and Perdita compared with Puck and Miranda. See Figure \ref{fig:spectrum} caption for data sources. \label{tab:color}'
 
-code = 'Mab'
 constants_dict = {
     'Mab':{
         'H':{'stem':'urh', 'bp_file':paths.static / 'h.csv', 'A':1}, # for integrated I/F use area of 1 km
         'K':{'stem':'urk', 'bp_file':paths.static / 'kp.csv', 'A':1}, 
+        '500':[0.5, 50, 3],
         },
     'Ophelia':{
         'H':{},
@@ -37,61 +37,34 @@ constants_dict = {
     'Perdita':{
         'H':{'stem':'urh', 'bp_file':paths.static / 'h.csv', 'A':1}, 
         'K':{'stem':'urk', 'bp_file':paths.static / 'kp.csv', 'A':1}, 
+        '500':[0.5, 54, 22],
         },
 }
 
-for code in ['Perdita', 'Mab']:
-    # get sun-target and Earth-target distance from Horizons
-    obscode = '568'
-    date = '2019-10-28'
-    tstart = date+' 11:00' #this just needs to be approximate
-    tend = date+' 12:00'
-    horizons_obj = Horizons(
-        id=code,
-        location=obscode,
-        epochs={"start": tstart, "stop": tend, "step": "1h"},
-    )
-    ephem = horizons_obj.ephemerides()[0]
-    target_sun_dist = ephem['r']
-    target_obs_dist = ephem['delta']
-    area_km = constants_dict[code]['H']['A']
-    target_omega = area_km*u.km**2 / (((target_obs_dist*u.au).to(u.km))**2) #setting area to 1 km2 means that I/F function will output integrated I/F
+def quadsum(err1, err2):
+    return np.sqrt(err1**2 + err2**2)
     
-    if code == 'Mab':
-        wls, fluxes, errs = [], [], []
-    for band in ['H', 'K']:
[…]

### 2023-07-22 src/scripts/detection_pretty_picture.py

@@ -43,8 +43,8 @@ constants_dict = {
         'K':{},
         },
     'Perdita':{
-        'H':{},
-        'K':{},
+        'H':{'stem':'urh', 'coadds':6, 'xpos':262, 'ypos':306},
+        'K':{'stem':'urk', 'coadds':4, 'xpos':497, 'ypos':973},
         },
 }
 

### 2023-07-22 src/scripts/path_on_detector.py

@@ -8,7 +8,8 @@ import os
 import pandas as pd
 from astroquery.jplhorizons import Horizons
 from datetime import datetime, timedelta
-from pylanetary.planetnav import *
+from pylanetary.navigation import *
+from pylanetary.utils import Body
 import astropy.units as u
 
 '''
@@ -137,14 +138,16 @@ dist = d_AU.to(u.km).value
 pixscale_km = dist*np.tan(np.deg2rad(pixscale_arcsec/3600.))
 #print(f'pixel scale is {pixscale_km} km')
 
-nav = PlanetNav(data, ephem[0], req, rpol, pixscale_arcsec)
+ura = Body('Uranus', epoch=obs_time, location='568') #Keck
+nav = Nav(data, ura, pixscale_arcsec)
+#ephem = nav.ephem
 dx_canny, dy_canny, _, _ = nav.colocate(mode='canny',
                     low_thresh=1e-5, 
                     high_thresh=0.01, 
                     sigma=5, 
                     tb=1600, 
                     a=0.1, 
-                    beamsize=0.1,
+                    beam=0.1,
                     diagnostic_plot=False)
 
 ctr = (data.shape[0]/2 + dx_canny, data.shape[1]/2 + dy_canny)
@@ -173,6 +176,18 @@ ax.set_xlabel('Pixels', fontsize = fs)
 ax.set_ylabel('Pixels', fontsize = fs)
 ax.tick_params(which='both', labelsize = fs - 2)
 ax.legend()
+
+# add annotation for Miranda and Puck
+ax.annotate('Puck', (233, 275), xytext=(260,230), 
+            color='cyan', 
+            fontsize=fs, 
+            arrowprops={'width':1, 'color':'cyan', 'headwidth':6, 'headlength':10}, 
+            transform=ax.transAxes)
+ax.annotate('Miranda', (75, 93), xytext=(90,40), 
+            color='cyan', 
+            fontsize=fs, 
+            arrowprops={'width':1, 'color':'cyan', 'headwidth':6, 'headlength':10}, 
+            transform=ax.transAxes)
 
 plt.tight_layout()
 fig.savefig(paths.figures / f"motion_on_detector_{code}.png", dpi=300)

### 2023-07-22 src/scripts/perdita_intif_calc.py

@@ -1,0 +1,23 @@
+#!/usr/bin/env python
+
+import numpy as np
+
+'''
+very simple script to compute Perdita's integrated I/F with error based on what is in
+Karkoschka 01
+'''
+
+a16 = 0.033 #average Portia group reflectivity at alpha=16 degrees
+phase_corr = 2.2 #from Portia group curve in other Karkoschka01 paper
+
+radius = 15 #km
+r_err = 3 #assuming this includes the uncertainty on a16
+
+intifs = []
+for r in [radius - r_err, radius, radius+r_err]:
+    
+    A = np.pi*r**2
+    intif = A*a16*phase_corr
+    intifs.append(intif)
+    
+print(intifs[1], intifs[1]-intifs[0], intifs[2]-intifs[1])

### 2023-07-22 src/scripts/photometric_uncertainty_disk.py

@@ -1,0 +1,114 @@
+#!/usr/bin/env python
+
+'''
+Use the frame-by-frame flux variations in a cloudless region on the planet Uranus 
+in both H and Kp band to derive uncertainty in the photometry
+
+The night was very photometrically stable. We derived the photometric uncertainty 
+by looking at the frame-by-frame surface brightness variations of cloud-free regions
+of the planet. We determined the surface brightness of the planet in two 20x20 pixel regions
+of the disk in both H- and Kp-band, one just north of Uranus's equator, and one just south 
+of the pole. The frame-by-frame variance displayed no clear temporal trends in either H- or Kp-band;
+the fluctuations looked like Gaussian noise with standard deviations of 2.1\% in H-band and 5.0\% 
+in Kp-band. These numbers agree with the spread in the fluxes derived from the three standard star
+frames.
+'''
+
+from shift_stack_moons.image import *
+from shift_stack_moons.shift_stack_moons import *
+import warnings, paths, os
+
+
+constants_dict = {
+    'Mab':{
+        'H':{'stem':'urh', 'pos1':(550, 500), 'pos2':(735, 485), 'edge_detect':False},
+        'Kp':{'stem':'urk', 'pos1':(615, 500), 'pos2':(770, 470),'edge_detect':True},
+        },
+    'Ophelia':{
+        'H':{},
+        'Kp':{},
+        },
+    'Cupid':{
+        'H':{},
+        'Kp':{},
+        },
+    'Perdita':{
+        'H':{},
+        'Kp':{},
+        },
+}
+
+# find filenames
+code = 'Mab'
+data_dir = paths.data / 'reduced/2019oct28'
+data_files = os.listdir(data_dir)
+obscode = '568'
+date = '2019-10-28'
+tstart = date+' 00:00'
+tend = date+' 23:59'
+pixscale = 0.009971
+boxsize = 10
+
+
+for band in ['H', 'Kp']:
+    print(f"Starting {code} {band}-band")
+    stem = constants_dict[code][band]['stem']
+    edge_detect = constants_dict[code][band]['edge_detect']
+    
+    fname_list = [data_dir / s for s in data_files if s.startswith(stem)]
+    
+    # first align them as we do for the shift-and-stack
+    frames = [Image(fname).data for fname in fname_list]
[…]

### 2023-07-22 src/scripts/photometry.py

@@ -21,7 +21,6 @@ import paths
 from scipy.interpolate import interp1d
 
 
-fluxcal_frac_err = 0.10 #check this number!
 photometry_constants_dict = {
     'Mab':{
         'H':{'stem':'urh', 'coadds':6, 'C1':8.87e-17, 'xpos':187, 'ypos':395}, #urh156
@@ -49,6 +48,24 @@ def get_wing_corr(r, wing_corrs):
     return np.mean(np.array([corr0, corr1, corr2]))
 
 
+def compute_ul(rms, psf, nsigma = 3):
+    '''
+    Determine upper limit given the RMS noise in the image
+    This is according to Imke's method, which was used but not explained
+        very well in Paradis+19
+    Basically assume the peak value of the PSF is at 3 sigma RMS, then figure
+        out what the total flux would be that makes such a PSF
+    
+    rms: float, required.
+    psf: np array, required.
+    nsigma: float, optional. significance you want to compute.
+    '''
+    psf /= np.max(psf)
+    psf *= (rms * nsigma)
+    ul = np.sum(psf)
+    
+    return ul
+
 ## compute the photometry for many inner and outer radii
 nsamples = 50
 ri0 = 3
@@ -64,6 +81,11 @@ for code in ['Mab', 'Perdita']:
         ypos = photometry_constants_dict[code][band]['ypos'] 
         # Paradis et al conversion factors for 2019-10-28
         C1 = photometry_constants_dict[code][band]['C1']  # from cts s-1 to erg s-1 cm-2 um-1; see Paradis+23 Section 2.5.1
+        
+        # bring in the photometric uncertainty from photometric_uncertainty_disk.py
+        with open(paths.output / f"{stem}_photometric_uncertainty_percent.txt", "r") as f:
+            fluxcal_frac_err = 0.01*float(f.readline())
+        print(fluxcal_frac_err)
         
         fname = paths.data / f'results/{stem}_{code}_2019-10-28.fits'
         CU, CR = 1,1 # see Paradis+23 Section 2.5. this could be looked at later but for now it's ok
@@ -141,17 +163,18 @@ for code in ['Mab', 'Perdita']:
         final_flux = np.mean(results_table)
         final_err = np.abs(np.percentile(results_table, [16, 84]) - final_flux)
         final_std = np.std(results_table)
-        print(f'{code} flux = {final_flux} erg s-1 cm-1 um-1')
[…]

### 2023-07-22 src/scripts/plot_perturbation_experiment.py

@@ -43,8 +43,8 @@ from mpl_toolkits.axes_grid1.axes_divider import make_axes_locatable
 code = 'Mab'
 constants_dict = {
     'Mab':{
-        'H':{'stem':'urh', 'xpos':187, 'ypos':395}, #urh156
-        'K':{'stem':'urk', 'xpos':188, 'ypos':307}, #urk146
+        'H':{'stem':'urh', 'coadds':6, 'C1':8.87e-17, 'xpos':187, 'ypos':395}, #urh156
+        'K':{'stem':'urk', 'coadds':4, 'C1':6.46e-17, 'xpos':188, 'ypos':307}, #urk146
         },
     'Ophelia':{
         'H':{},
@@ -82,13 +82,17 @@ for band in ['H', 'K']:
     
     data_real = data_real[ypos-box_y:ypos+box_y, xpos-box_x:xpos+box_x]
     cs_conv_real = difference_of_gaussians(data_real, sigma_inner, sigma_outer)
-    ## print(np.sum(data_real)/np.sum(cs_conv_real)) #this does not conserve flux
-    ## see workaround below: we can scale both the signal and the noise by the bin size
-    ## and then we can take the noise level from the binned data
+    print(np.sum(data_real), np.sum(cs_conv_real)) #this does not conserve flux!
+    ## see workaround below: just rescale by std of data and farmes
 
     # rebin factor of z
-    cs_rebin_real=zfactor**2*rebin(cs_conv_real, 1/zfactor) #factor of z**2 to conserve flux
-    detection_real = np.max(cs_rebin_real)/(np.std(cs_rebin_real) / zfactor) #by binning, we are increasing signal by factor of z^2 so snr increases by factor of z
+    cs_rebin_real=rebin(cs_conv_real, 1/zfactor) #this step does conserve flux
+    detection_real = np.max(cs_rebin_real) /(np.std(cs_rebin_real))
+    
+    # this scaling is inconsistent with Imke's solution for upper limits
+    # need to instead convert this to the nsigma of the maximum single pixel
+    # or rescale Imke's version so that we compare the per-pixel RMS 
+    # with the total area of the psf
     
     detection_sizes = []
     for i in range(100):
@@ -96,10 +100,10 @@ for band in ['H', 'K']:
         data = fits.open(fname)[0].data
         data = data[ypos-box_y:ypos+box_y, xpos-box_x:xpos+box_x]
[…]

### 2023-07-22 src/scripts/psf_wing_correction.py

@@ -18,15 +18,17 @@ ready to ship!
 if not os.path.exists(paths.data / "tables"):
     os.mkdir(paths.data / "tables")
 
+psf_cutout_size = 31 #should be odd
 
 show_figures = False
 for filt in ['H', 'K']:
 
     nsamples = 50
     ri0 = 3 #smallest moon aperture radius
-    ri1 = 20 #largest moon aperture radius
-    ro0 = 150 #star aperture radius to capture all star flux; also sets inner radius of noise annulus
-    ro1 = 200
+    ri1 = 10 #largest moon aperture radius
+    ro0 = 15
+    ro1 = 50
+    ro_star = 150 #star aperture radius to capture all star flux; also sets inner radius of noise annulus
     noise_ann_width = 50 #width of noise annulus starting at ro
     
     star_files = [paths.data / f"reduced/2019oct28" / s for s in os.listdir(paths.data / f"reduced/2019oct28/") if s.startswith(f'hd{filt}')]
@@ -34,7 +36,7 @@ for filt in ['H', 'K']:
     ros = np.linspace(ro0, ro1, nsamples)
     
     star_cts = []
-    star_errs = []
+    #star_errs = []
     for k, fname in enumerate(star_files):
         
         hdul = fits.open(fname)
@@ -46,47 +48,50 @@ for filt in ['H', 'K']:
             cutoff = 2500
         data[data>cutoff] = 0 #this removes bad pixels
         star_pos = np.unravel_index(np.argmax(data), data.shape)[::-1]
-        #print(star_pos, np.max(data))
+        print(star_pos, np.max(data))
+        
+        # save a point-spread function
+        sz = int((psf_cutout_size-1)/2)
+        psf_cutout = data[star_pos[1]-sz:star_pos[1]+sz, star_pos[0]-sz:star_pos[0]+sz]
+        if not os.path.exists(paths.data / 'psfs'):
+            os.mkdir(paths.data / 'psfs')
+        np.save(paths.data / f'psfs/psf_{filt}_{k}.npy', psf_cutout)
         
         # flux from moon inner radius
         moon_aps = np.array([aperture.CircularAperture(star_pos, r=ri) for ri in ris])
         moon_areas = np.array([ap.area for ap in moon_aps])
         moon_apsums = np.array([aperture.ApertureStats(data, ap).sum for ap in moon_aps])
         
-        # flux from star inner radius
[…]
